We now compare two norm/topology controls used in the construction:
the dyadic insertion seminorm (a polymer/RG seminorm used to bound inserted observables scale-by-scale) and
the Osterwalder--Schrader (OS) seminorm used for OS reconstruction.
The key estimate is a one-way bound
\[
\|R_{*,t}\|_{\mathrm{OS};k,K,\varepsilon}\le C_{\mathrm{OS}\leftarrow\mathrm{ins}}\,
\|R_{*,t}\|_{\mathrm{ins};\mu;k,K,\varepsilon},
\]
showing that insertion-seminorm control implies OS-seminorm control for the same remainder observable $R_{*,t}$.
This is Lemma~\ref{lem:ins_to_OS} below.

\paragraph{What proves.}
Under the \emph{patched-chart} (good-block + good-flow) expectation state $\langle\cdot\rangle^{\mathrm{good}}$,
we prove a uniform constant $C_{\mathrm{OS}\leftarrow\mathrm{ins}}$ (independent of scale $j$ and lattice spacing $a$) such that for any
positive-time insertion activity $J$,
\[
\|F_J\|_{\mathrm{OS};k,K,\varepsilon}\ \le\ C_{\mathrm{OS}\leftarrow\mathrm{ins}}\ \|J\|_{\mathrm{ins};j;k,K,\varepsilon},
\]
where $F_J(f):=\sum_{X}J(X;f)$ is the associated observable.

\paragraph{Interpretation.}
The OS seminorm is controlled by a \emph{supremum} bound on $F_J$; under the patched-chart state the field space is compact on each relevant block,
so the local functional seminorm controls the sup norm.
Polymer weights and counting convert this local bound into a bound for the full summed observable.

Let $\langle\cdot\rangle^{\mathrm{good}}$ be the patched-chart (good-event, chart-truncated) expectation state $\langle\cdot\rangle^{\mathrm{good}}$.
Let $\Theta$ denote Euclidean time reflection and $\mathcal A_+$ the positive-time algebra.

For $F\in\mathcal A_+$ define
\[
\|F\|_{\mathrm{OS}}:=\sqrt{\langle \Theta F\cdot F\rangle^{\mathrm{good}}}.
\]
Fix $\varepsilon>0$ and compact $K\subset\{x_0\ge \varepsilon\}$ and define the OS seminorm (Lane~A topology)
\[
\|F\|_{\mathrm{OS};k,K,\varepsilon}
:=\sup\{\|F(f)\|_{\mathrm{OS}}:\ \mathrm{supp}(f)\subset K,\ |f|_{C^k(K)}\le 1\}.
\]

At dyadic scale $j$, an insertion activity is a family $J=\{J(X;f)\}_{X\in\mathscr P_j}$ supported on $j$-polymers.
The insertion seminorm is
\begin{equation}
\|J\|_{\mathrm{ins};j;k,K,\varepsilon}
:=
\sup_{\substack{f:\ \mathrm{supp}(f)\subset K\\ |f|_{C^k(K)}\le 1}}
\ \sup_{X\in\mathscr P_j}\ 
\Gamma_j(X)^{-1}\ \|J(X;f)\|_j,
\end{equation}
with polymer weight $\Gamma_j(X)=A^{|X|_j}$ for some fixed $A>1$ and local functional seminorm $\|\cdot\|_j$.

\begin{lemma}[OS bound by $L^\infty$]\label{lem:OS_by_sup}
For any $F\in\mathcal A_+$,
\[
\|F\|_{\mathrm{OS}}\le \|F\|_{L^\infty(\Omega)},
\]
where the sup is over the underlying configuration space $\Omega$ on which the patched probability measure is supported.
\end{lemma}

\begin{proof}
Since $\langle\cdot\rangle^{\mathrm{good}}$ is a probability expectation and $|\Theta F|=|F|$ pointwise,
\[
\|F\|_{\mathrm{OS}}^2=\langle \Theta F\cdot F\rangle^{\mathrm{good}}
\le \langle |F|^2\rangle^{\mathrm{good}}
\le \|F\|_\infty^2.
\]
Take square roots.
\end{proof}

On the patched-chart state, configurations in each unit block satisfy a fixed exponential chart bound, hence belong to a compact set.
Local functionals are smooth functions on a finite-dimensional compact manifold.

\begin{proposition}[Supremum control by the local seminorm (proved in Proposition~\ref{ass:seminorm_axioms})]\label{ass:sup_from_local}
There exists a constant $C_\infty$ independent of $j$ and $a$ such that for any local functional $F$ supported in a single $j$-block,
\[
\|F\|_{\infty}\le C_\infty\,\|F\|_j.
\]
More generally, for $F$ supported in a $j$-polymer $X$,
\[
\|F\|_\infty\le C_\infty\,\Gamma_j(X)\,\|F\|_j,
\]
where $\Gamma_j(X)$ is the polymer weight used in the definition of $\|\cdot\|_j$.
\end{proposition}

now justified by compactness of the patched-chart configuration space.

Given an insertion activity $J$, define the associated observable
\[
F_J(f):=\sum_{X\in\mathscr P_j} J(X;f),
\]
with the sum restricted to polymers intersecting the $j$-neighborhood of $\mathrm{supp}(f)$ (finite by construction).

\begin{proposition}[Marked-polymer counting (proved in Proposition~\ref{ass:seminorm_axioms})]\label{ass:counting}
There exists $C_{\mathrm{count}}$ independent of $j$ and $a$ such that for any polymer weights $\Gamma_j$,
\[
\sum_{X\ni x} \Gamma_j(X)\ \le\ C_{\mathrm{count}},
\]
uniformly in the lattice site $x$ and uniformly in $j$.
(The same constant controls polymer sums for insertions supported near a fixed compact $K$.)
\end{proposition}

It is purely combinatorial.

\begin{theorem}[Insertion seminorm $\Rightarrow$ OS seminorm]\label{thm:ins_to_OS}\label{lem:ins_to_OS}
Assume \ref{ass:sup_from_local} and \ref{ass:counting}. Then for each dyadic scale $j$ and each insertion activity $J$ supported in the positive-time region,
\[
\|F_J\|_{\mathrm{OS};k,K,\varepsilon}
\le C_{\mathrm{OS}\leftarrow\mathrm{ins}}\ \|J\|_{\mathrm{ins};j;k,K,\varepsilon},
\]
with explicit constant
\begin{equation}\label{eq:C_OS_ins}
C_{\mathrm{OS}\leftarrow\mathrm{ins}}
:= C_\infty\,C_{\mathrm{count}}.
\end{equation}
The constant is independent of $j$ and independent of lattice spacing $a$ under the patched-chart construction.
\end{theorem}

\begin{proof}
Fix $f$ with $\mathrm{supp}(f)\subset K$ and $|f|_{C^k}\le 1$.
By Lemma~\ref{lem:OS_by_sup},
\[
\|F_J(f)\|_{\mathrm{OS}}\le \|F_J(f)\|_\infty \le \sum_X \|J(X;f)\|_\infty.
\]
Apply Proposition~\ref{ass:sup_from_local}:
\[
\|J(X;f)\|_\infty \le C_\infty\,\Gamma_j(X)\,\|J(X;f)\|_j.
\]
By the definition \eqref{eq:ins_norm},
$\|J(X;f)\|_j\le \Gamma_j(X)\,\|J\|_{\mathrm{ins};j;k,K,\varepsilon}$.
Hence
\[
\|F_J(f)\|_{\mathrm{OS}}
\le C_\infty\,\|J\|_{\mathrm{ins};j;k,K,\varepsilon}\ \sum_X \Gamma_j(X).
\]
The sum is over polymers intersecting the fixed neighborhood of $K$; by Proposition~\ref{ass:counting} it is bounded by $C_{\mathrm{count}}$.
Taking the supremum over $f$ yields the claim with constant $C_\infty C_{\mathrm{count}}$.
\end{proof}



\begin{corinsword}[Fixed bounded-word variant of Theorem~\ref{thm:ins_to_OS}]\label{cor:ins_to_OS_bounded_word}
Fix a dyadic scale $j$, a compact $K_f\subset\{x_0\ge \varepsilon\}$, and an insertion activity
$J=\{J(X;f)\}_{X\in\mathscr P_j}$ supported on polymers intersecting the $j$-neighborhood of $K_f$.
Let
\[
\mathbf B=(B_0,\dots,B_q)
\]
be a fixed finite family of bounded positive-time cylinder / flowed observables, and let
$K_{B,f}\subset\{x_0\ge \varepsilon\}$ be a compact neighborhood containing $K_f$ together with the supports of all $B_r$.
For each scale $j$, choose a fixed finite $j$-polymer neighborhood $X_{B,f}(j)$ covering the additional support carried by the word $\mathbf B$ and define the bounded-word insertion activity by
\[
J^{\mathbf B}(X\cup X_{B,f}(j);f):=B_0\,J(X;f)\,B_1\cdots B_q.
\]
Then there exists a constant
\[
C_{\mathrm{word}}(K_{B,f};\mathbf B^{\sharp})\ge 1,
\qquad
\mathbf B^{\sharp}:=(B_0^{\sharp},\dots,B_q^{\sharp}),
\]
depending only on the normalized fixed word $\mathbf B^{\sharp}$ and on the support neighborhood $K_{B,f}$, but independent of $J$, $j$, and $a$, such that
\begin{equation}\label{eq:ins_word_bound}
\|J^{\mathbf B}\|_{\mathrm{ins};j;k,K_{B,f},\varepsilon}
\le
C_{\mathrm{supp}}(K_{B,f})\,
C_{\mathrm{word}}(K_{B,f};\mathbf B^{\sharp})\,
\Bigl(\prod_{r=0}^{q}\|B_r\|_\infty\Bigr)\,
\|J\|_{\mathrm{ins};j;k,K_f,\varepsilon}.
\end{equation}
Consequently,
\begin{equation}\label{eq:OS_word_bound}
\|F_{J^{\mathbf B}}\|_{\mathrm{OS};k,K_{B,f},\varepsilon}
\le
C_{\mathrm{OS}\leftarrow\mathrm{ins}}\,
C_{\mathrm{supp}}(K_{B,f})\,
C_{\mathrm{word}}(K_{B,f};\mathbf B^{\sharp})\,
\Bigl(\prod_{r=0}^{q}\|B_r\|_\infty\Bigr)\,
\|J\|_{\mathrm{ins};j;k,K_f,\varepsilon}.
\end{equation}
\end{corinsword}

\begin{proof}
If one of the factors $B_r$ vanishes then both claims are immediate, so assume $B_r\neq 0$ and write
\[
B_r=\|B_r\|_\infty\,B_r^{\sharp},
\qquad
\|B_r^{\sharp}\|_\infty=1.
\]
Adjoining the fixed support carried by the bounded word enlarges every marked polymer only by the fixed finite neighborhood $X_{B,f}(j)$.
Therefore the associated polymer weight changes by at most a uniform support factor,
\[
\Gamma_j\bigl(X\cup X_{B,f}(j)\bigr)
\le
C_{\mathrm{supp}}(K_{B,f})\,\Gamma_j(X),
\]
with $C_{\mathrm{supp}}(K_{B,f})$ depending only on the chosen support neighborhood and not on $J$, $j$, or $a$.
On the patched-chart compact set, the fixed normalized factors $B_r^{\sharp}$ have bounded local seminorms on $K_{B,f}$; iterating the local product / regularity axioms therefore yields a constant
$C_{\mathrm{word}}(K_{B,f};\mathbf B^{\sharp})$ such that for every marked polymer term,
\[
\bigl\|B_0\,J(X;f)\,B_1\cdots B_q\bigr\|_j
\le
C_{\mathrm{word}}(K_{B,f};\mathbf B^{\sharp})\,
\Bigl(\prod_{r=0}^{q}\|B_r\|_\infty\Bigr)
\|J(X;f)\|_j.
\]
Combining the last two displays and taking the supremum in the insertion norm \eqref{eq:ins_norm} gives \eqref{eq:ins_word_bound}.
Applying Theorem~\ref{thm:ins_to_OS} to the modified activity $J^{\mathbf B}$ then gives \eqref{eq:OS_word_bound}.
\end{proof}

\begin{corollary}[OS control of the insertion RG remainder]\label{cor:A1_bridge}
Let $\mathcal R_{*,t}$ be the insertion RG remainder at matching scale $\mu$ from Theorem~\ref{thm:ins_decomp}.
Under the patched-chart state and the hypotheses of Theorem~\ref{thm:ins_to_OS},
\[
\|\mathcal R_{*,t}\|_{\mathrm{OS};k,K,\varepsilon}
\le C_{\mathrm{OS}\leftarrow\mathrm{ins}}\ \|\mathcal R_{*,t}\|_{\mathrm{ins};\mu;k,K,\varepsilon}.
\]
Thus the insertion-norm remainder bound converts directly into the A1 OS-seminorm remainder bound.
\end{corollary}

\begin{remark}[End of the insertion-to-OS transfer]
Theorem~\ref{thm:ins_to_OS}, Corollary~\ref{cor:ins_to_OS_bounded_word}, and Corollary~\ref{cor:A1_bridge} give an explicit comparison between the insertion seminorm
and the OS seminorm for positive-time insertions supported in $K$, both in the basic single-insertion channel and after adjoining a fixed bounded positive-time word.  In particular, insertion-RG remainder bounds
translate directly into OS-seminorm remainder bounds.
Combined with the coefficient invertibility bounds of Section~4.7 (Corollary~\ref{cor:Lambda}), this completes the
Lane-A small-flow-time convergence argument.  De-patching to the physical Wilson state is handled by
Lemmas~\ref{lem:depatch_block} and \ref{lem:depatch_continuum} in Section~\ref{sec:patching}.
\end{remark}

