Lane~A's flow-localization bounds for the probes $\cO_{S,t}$ and $\cO_{Q,t}$ require the Gaussian off-diagonal bounds
\eqref{eq:K_gauss}--\eqref{eq:K_der_gauss} for the fundamental solution of the linearized DeTurck evolution.

Under the bounded-regime hypothesis~\ref{ass:bounded_regime}, the DeTurck-flowed gauge potential remains inside a fixed exponential chart on $(0,t_\ast]$
and satisfies deterministic pointwise bounds on a finite set of local derivatives.
As a consequence, the coefficients of the linearized equation are bounded (with at most time-integrable singularities inherited from $\|\nabla B(t)\|_\infty\lesssim t^{-1/2}$).

\paragraph{Status in this submission.}
The bounded-regime hypothesis~\ref{ass:bounded_regime} is verified on the good-flow chart event by Lemma~\ref{lem:chart_persist}
(Section~\ref{sec:good_flow_chart}); the contribution of the complement is absorbed in expectations by Corollary~\ref{cor:superpoly_flow}.

For the parametrix method, it is convenient to rewrite first-order terms in divergence form.

\begin{lemma}[Divergence-form reduction and coefficient bounds]\label{lem:div_form_reduction}
Let $\psi$ solve the linearized DeTurck system
\[
\partial_t \psi
=
\Delta \psi + \sum_{\alpha=1}^4 A_\alpha(t,x)\,\partial_\alpha\psi + V(t,x)\,\psi
\]
on $0<s<t\le t_\ast$, where $A_\alpha,V\in \mathrm{End}(V)$.
Assume that under the bounded-regime hypothesis~\ref{ass:bounded_regime} the coefficients obey
\[
\|A_\alpha(t,\cdot)\|_\infty\le \mathsf A_0,\qquad
\|V(t,\cdot)\|_\infty\le \mathsf V_0+\mathsf V_1\,t^{-1/2},
\qquad
\|\partial_\alpha A_\alpha(t,\cdot)\|_\infty\le \mathsf A_1\,t^{-1/2}.
\]
Then $\psi$ also satisfies the divergence-form system
\begin{equation}\label{eq:div_form_lin}
\partial_t \psi
=
\Delta \psi + \sum_{\alpha=1}^4 \partial_\alpha\big(A_\alpha(t,x)\psi\big)+W(t,x)\psi,
\end{equation}
with
\[
W(t,x):=V(t,x)-\sum_{\alpha=1}^4\partial_\alpha A_\alpha(t,x),
\qquad
\|W(t,\cdot)\|_\infty\le \mathsf W_0+\mathsf W_1\,t^{-1/2},
\]
where $\mathsf W_0=\mathsf V_0$ and $\mathsf W_1=\mathsf V_1+4\mathsf A_1$.
\end{lemma}

\begin{proof}
Use $A_\alpha\partial_\alpha\psi=\partial_\alpha(A_\alpha\psi)-(\partial_\alpha A_\alpha)\psi$ and regroup terms.
\end{proof}

\paragraph{Comment.}
In the concrete setting, $A_\alpha$ and $V$ are smooth functions of the background field $B(t)$ and its first derivatives
(DeTurck gauge).
Under Proposition~\ref{ass:bounded_regime}, $\|B(t)\|_\infty\le M_0$ and $\|\nabla B(t)\|_\infty\le M_1 t^{-1/2}$ on $(0,t_\ast]$,
so the bounds in Lemma~\ref{lem:div_form_reduction} hold with explicit $\mathsf A_0,\mathsf V_0,\mathsf V_1,\mathsf A_1$
depending on $(M_0,M_1)$ and universal Lie/gauge constants.

\begin{theorem}[Gaussian kernel bounds for \eqref{eq:div_form_lin}]\label{thm:gauss_continuum_parametrix}
Assume the hypotheses of Lemma~\ref{lem:div_form_reduction}.
Let $K(t,s;x,y)$ be the fundamental solution (matrix kernel) of \eqref{eq:div_form_lin}.
Then there exist constants $c_1\in(0,1)$ and, for each $m\in\{0,1,\dots,m_{\max}\}$, constants $C_m<\infty$ depending only on
\[
(d=4,\dim V,\mathsf A_0,\mathsf W_0,\mathsf W_1,t_\ast,m_{\max}),
\]
such that for all $0<s<t\le t_\ast$ and all $x,y\in\mathbb R^4$,
\begin{align}
\|K(t,s;x,y)\|_{\mathrm{op}}
&\le
C_0\,(t-s)^{-2}\exp\!\Big(-c_1\,\frac{|x-y|^2}{t-s}\Big),\\
\|\nabla_x^m K(t,s;x,y)\|_{\mathrm{op}}
&\le
C_m\,(t-s)^{-(2+m/2)}\exp\!\Big(-c_1\,\frac{|x-y|^2}{t-s}\Big).
\end{align}
\end{theorem}

\begin{proof}
This is proved by a Picard/parametrix expansion around the heat kernel, with explicit control of the Volterra majorant generated by
the $(t-r)^{-1/2}$ singularity coming from the divergence-form first-order term.
A fully written proof with constant dependence is given in Appendix~\ref{app:kernel_parametrix}
(Theorem~\ref{thm:gauss_cont_proved}); the bounds above are the specialization to $d=4$ with the exponential dependence
absorbed into the constants $C_m$ for $t\le t_\ast$.
\end{proof}

On $a\mathbb Z^4$ the DeTurck flow is implemented with finite-range difference operators.
The linearized evolution takes the form
\[
\partial_t\psi
=
\Delta_a\psi+\sum_{\alpha=1}^4\nabla_{a,\alpha}\big(A_{\alpha,a}(t,x)\psi\big)+W_a(t,x)\psi,
\]
with the same uniform coefficient bounds as in Lemma~\ref{lem:div_form_reduction} under Proposition~\ref{ass:bounded_regime}.

Once one inputs the uniform lattice heat-kernel bounds proved internally in Appendix~\ref{app:discrete_heat_kernel}
(Theorem~\ref{thm:lattice_gauss_uniform}), the lattice parametrix proof in Appendix~\ref{app:discrete_parametrix} yields
\eqref{eq:K_gauss}--\eqref{eq:K_der_gauss} with constants independent of $a$ (for $t-s\ge a^2$ and $x,y$ in the compact support region of the observable family).
In particular, the ``discrete input'' used here is now fully closed within this submission.

Under the bounded-regime hypothesis~\ref{ass:bounded_regime}, Lemma~\ref{lem:div_form_reduction} supplies the coefficient bounds required by the parametrix theorem.
Therefore Proposition~\ref{ass:gaussian_kernel} holds (in the continuum and, with the discrete heat kernel input, uniformly in $a$),
closing the flow-localization lemma stack needed for Theorem~\ref{thm:flow_local_v91}.
