
\documentclass[11pt]{article}
\input{support/support_style}
\input{support/support_metadata}
\begin{document}

\SupportTitleBlock
  {JMP Analytic Certification Dossier}
  {Reserve analytic-route summary synchronized to the Phase-IX-hardened JMP submission bundle.}
  {\ReserveOnlyNote\ This dossier summarizes the theorem-facing analytic route already carried by the live proof homes and the synchronized proof-kernel extraction. It is not a second proof and adds no new mathematics. Updated \SyncDate.}

\section{Current synchronization baseline}

\SupportLead{This version is keyed to the final Phase-IX bundle rather than the earlier 368-page repaired suite. The live proof burden still lies only in the four proof-home roots; the proof kernel and the Phase-IX closure gate are derived audit roots retained for expert circulation and package-level sign-off.}

\begin{center}
\small
\begin{tabularx}{\linewidth}{@{}L{2.8cm}Y C{1.0cm}@{}}
\toprule
\textbf{Component} & \textbf{Current function in the synchronized bundle} & \textbf{Pages}\\
\midrule
\rowcolor{AccentLight}\multicolumn{3}{@{}l@{}}{\textbf{Live proof-home suite}}\\
Core paper & States the exact theorem object, packet reduction, seam nodes, claim boundaries, and the assembly proof. & \CorePages\\
Companion I & Proof home for the ultraviolet/public-scope gate, one-shot entrance, fixed-lattice gap, same-scale Wilson return, QE3 chain, and continuum transport. & \CompanionIPages\\
Companion II & Proof home for Packet~4 front end and for the capwise-to-full sharp-local construction machinery, including the theorem-facing finite-cap bridge into Theorem~5.74. & \CompanionIIPages\\
Companion III & Proof home for the OS/Wightman endpoint, non-triviality, qualitative faithful-Wilson universality, and the exact local-net endpoint. & \CompanionIIIPages\\
\midrule
\rowcolor{AccentLight}\multicolumn{3}{@{}l@{}}{\textbf{Derived audit roots (not proof homes)}}\\
Proof kernel & Expert-audit extraction of the load-bearing packet route, import boundary, exclusions boundary, and synchronized attack-line map. & \ProofKernelPages\\
Phase-IX closure gate & Package-level closure checklist, theorem-node matrix, submission inventory, and final closure memo. & \PhaseIXPages\\
\bottomrule
\end{tabularx}
\end{center}

The proof-home suite is \ProofHomeTotal\ pages. Including the proof kernel and the Phase-IX closure gate, the packaged Overleaf bundle is \FullBundleTotal\ pages before reserve support papers.

\section{Continuous positive lower-bound route}

In compressed theorem-facing form, the explicit quantitative Route~1 certificate still has the shape
\[
\begin{aligned}
  c_{\mathrm{A1}}(G,\rho)>0
    &\Longrightarrow q^{\ast}(G,\rho)\in(0,1)
     \Longrightarrow m_{\mathrm{blk}}(G,\rho):=-\log q^{\ast}(G,\rho)>0,\\
    &\Longrightarrow m_{\ast}(G,\rho;u_{\mathrm{ren}})
      =\frac{m_{\mathrm{blk}}(G,\rho)}{2\,\mathrm{Cent}(G,\rho)\,\ell_0}>0,
\end{aligned}
\]
and the same $m_{\ast}$ is then reused at QE3, at Euclidean clustering, and at the Minkowski Hamiltonian gap.

\begin{center}
\small
\begin{tabularx}{\linewidth}{@{}L{2.2cm}Y Y@{}}
\toprule
\textbf{Stage} & \textbf{Current theorem-facing role} & \textbf{Live proof home}\\
\midrule
Ultraviolet gate & Compact-simple A1 bound and public group-scope export. & Core Section~3; proof in Companion~I\\
Entrance & One-shot entrance into the KP/Dobrushin basin at bounded physical scale. & Core Sections~3--4; proof in Companion~I\\
Fixed-lattice gap & Tuned full fixed-lattice OS gap together with the same-scale Wilson return. & Core Section~4; proof in Companion~I\\
Lane~A transport structure & Packet~4 front end, exact-dimension blocks, finite-truncation inverse control, finite-cap bridge 5.74A, finite-cap closure, bounded-state restriction compatibility, inductive-union passage, and bounded-base cyclicity. & Core Sections~5--6; proof homes in Companion~II, with the flowed de-patching seam in Companion~I Section~III\\
QE3 / continuum gap & Transport of the same $m_{\ast}$ to the continuum sharp-local vacuum sector. & Core Section~6; proof in Companion~I\\
OS / Wightman endpoint & Reuse of the same $m_{\ast}$ at Euclidean clustering and at the Minkowski Hamiltonian gap export. & Core Section~7; proof in Companion~III\\
Faithful-$\rho$ scope & Qualitative faithful-Wilson universality theorem together with the explicit statement that the quantitative ledger remains $\rho$-indexed. & Core Sections~1 and~7; proof in Companion~III\\
\bottomrule
\end{tabularx}
\end{center}

\section{Current seam-routing notes under the final bundle}

\begin{center}
\small
\begin{tabularx}{\linewidth}{@{}L{3.0cm}Y@{}}
\toprule
\textbf{Current manuscript-facing seam} & \textbf{Current synchronized route note}\\
\midrule
Finite-cap / engineering-cutoff removal & The lower bound $m_{\ast}$ is not read from capwise inverse constants. The Lane~A chain now runs theorem-facing through Corollary~F.330A, Theorem~F.331, promoted bridge 5.74A, Theorem~5.74, Corollary~5.75, Corollary~5.76, and Theorem~5.77 before the final spectral theorem is read.\\
Positive-flow-time inheritance & The public packet makes the flowed seam explicit: Packet~4 surfaces Theorem~4.92 together with Corollaries~4.93--4.95, and the Wilson/RG identification on $\mathcal A_{\mathrm{flow}}$ is routed through the flowed de-patching seam in Companion~I Section~III.\\
Continuum-limit survival & The live Route~1 chain is Core Theorem~IV.2 / Companion~I Theorem~III.18, then Theorems~F.211 and~F.212, Corollary~F.213, Lemma~F.214, Theorem~F.216, and Corollary~F.5; Theorem~F.298 remains the sole live weak-window sufficiency certificate on the public Route~1 spine.\\
Faithful-$\rho$ endpoint scope & The continuum local theory is theorem-level group-only only after qualitative faithful-Wilson universality, while the present explicit Route~1 quantitative certificate remains openly $\rho$-indexed.\\
Audit boundary & The proof kernel and the Phase-IX closure gate are synchronized with the same route, but neither one adds a new theorem edge. The kernel is an expert-audit extraction; the closure gate is a package-level sign-off document.\\
\bottomrule
\end{tabularx}
\end{center}

\section{Updated adversarial objection grid}

\begin{center}
\small
\begin{tabularx}{\linewidth}{@{}L{4.0cm}Y@{}}
\toprule
\textbf{Attack line} & \textbf{Current hardened-bundle answer path}\\
\midrule
A1. ``This proves only a fixed-lattice or prelimit gap.'' & Core Sections~4 and~6 plus Companion~I. The fixed-lattice lower bound is named on the Route~1 path and then explicitly transported to the continuum sharp-local Hilbert space.\\
A2. ``The finite-cap state / positivity bridge is still buried below Theorem~5.74.'' & Core Section~5 plus Companion~II. Packet~6 now surfaces the literal theorem-facing bridge F.331 $\to$ 5.74A $\to$ 5.74 $\to$ 5.75 $\to$ 5.76, and 5.74 cites that bridge directly.\\
A3. ``Capwise inverse-control constants may collapse the gap as $\Delta_{\max}\to\infty$.'' & Core Sections~5--6 plus Companion~II. Capwise inverse constants stay construction-local; the theorem-facing lower bound is read only after the full sharp-local passage and bounded-base cyclicity export.\\
A4. ``This proves only a fixed positive-flow-time statement.'' & Packet~4 plus Companion~I Section~III. The public packet explicitly exposes Theorem~4.92 together with Corollaries~4.93--4.95, and the flowed Wilson/RG identification on $\mathcal A_{\mathrm{flow}}$ is routed through the de-patching seam rather than left implicit.\\
A5. ``The OS/Wightman passage may weaken the rate after QE3.'' & Core Section~7 plus Companion~III. The same $m_{\ast}$ is reused through the Euclidean OS dossier, the Minkowski Hamiltonian transfer, and the non-triviality packet.\\
A6. ``Faithful-Wilson universality overclaims a faithful-$\rho$-uniform quantitative gap.'' & Core Sections~1 and~7 plus Companion~III. The qualitative universality theorem is explicit, and the quantitative Route~1 ledger remains openly $\rho$-indexed.\\
\bottomrule
\end{tabularx}
\end{center}

\section{Use and non-use rule}

Use this dossier only if an editor or referee asks for analytic-route detail. It should normally be sent together with the synchronized \emph{Referee Concordance and Reading Note}. If the request is for short-route expert audit, include the proof kernel. If the request is package-level sign-off or blocker closure, include \texttt{phase9\_closure\_gate.tex} or its compiled PDF as well.

\end{document}
