
\documentclass[11pt]{article}
\input{support/support_style}
\input{support/support_metadata}
\begin{document}

\SupportTitleBlock
  {JMP Referee Concordance and Reading Note}
  {Reserve document synchronized to the Phase-IX-hardened JMP submission bundle.}
  {\ReserveOnlyNote\ This note is organizational only. It aligns the current proof homes, packet map, and reading order with the final submission bundle and adds no new mathematics. Updated \SyncDate.}

\section{Current synchronization note}

This version matches the final bundle page counts and root structure: core \CorePages\ pages, Companion~I \CompanionIPages, Companion~II \CompanionIIPages, Companion~III \CompanionIIIPages, proof kernel \ProofKernelPages, and Phase-IX closure gate \PhaseIXPages. The proof-home suite is therefore \ProofHomeTotal\ pages, and the bundled Overleaf package is \FullBundleTotal\ pages before reserve support papers.

\begin{center}
\small
\begin{tabularx}{\linewidth}{@{}L{2.2cm}L{4.2cm}Y C{1.0cm}@{}}
\toprule
\textbf{Component} & \textbf{Current title} & \textbf{Intended role} & \textbf{Pages}\\
\midrule
Core paper & \CoreTitleText & Body-facing theorem paper: exact claim, packet reduction, seam nodes, endpoint framing, and assembly proof. & \CorePages\\
Companion I & \CompanionITitleText & Ultraviolet/public-scope gate and the full Route~1 mass-gap chain. & \CompanionIPages\\
Companion II & \CompanionIITitleText & Lane~A sharp-local construction, theorem-facing finite-cap bridge, finite-cap closure, inductive-union passage, and bounded-base cyclicity. & \CompanionIIPages\\
Companion III & \CompanionIIITitleText & Reconstruction, non-triviality, qualitative faithful-Wilson universality, and exact local-net endpoint. & \CompanionIIIPages\\
Proof kernel & \ProofKernelTitleText & Expert-audit extraction of the live packet route and the import / exclusion boundaries. & \ProofKernelPages\\
Phase-IX closure gate & \PhaseIXTitleText & Package-level pass conditions, closure matrix, submission inventory, and final checklist. & \PhaseIXPages\\
\bottomrule
\end{tabularx}
\end{center}

\section{Canonical source-to-bundle map}

\begin{center}
\small
\begin{tabularx}{\linewidth}{@{}L{4.2cm}Y Y@{}}
\toprule
\textbf{Canonical source region} & \textbf{Old function} & \textbf{Current proof home / synchronized bundle location}\\
\midrule
Sections~1--2 of monolith & Claim, scope, packet routing, and theorem-facing appendices. & Core paper Sections~1--2 and core appendices\\
Section~3 plus Appendices~F and~N & Ultraviolet gate, Wilson return, Route~1 transport, compact-simple A1 packet. & Companion~I; cited from Core Sections~3,~4, and~6\\
Sections~4--5 plus Appendix~L & Lane~A construction, finite truncation, mixed-channel bridge, bounded-state restriction compatibility, inductive-union passage, and cyclicity. & Companion~II; cited from Core Sections~5--6\\
Appendices~M and~O & OS/Wightman packet, non-triviality, faithful-Wilson universality, and endpoint packet. & Companion~III; cited from Core Section~7 and core Appendix~B\\
No monolithic equivalent (new extraction) & Minimal load-bearing theorem route for expert attack. & \texttt{proofkernel.tex}\\
No monolithic equivalent (new audit packet) & Final package-level pass conditions, blocker closure memo, and sign-off checklist. & \texttt{phase9\_closure\_gate.tex} plus repository-root Phase-VIII / Phase-IX memos\\
\bottomrule
\end{tabularx}
\end{center}

\section{Repair-sensitive public routing notes}

\begin{center}
\small
\begin{tabularx}{\linewidth}{@{}L{3.3cm}Y@{}}
\toprule
\textbf{Repair-sensitive public note} & \textbf{Current synchronized statement}\\
\midrule
Packet~4 visibility & Public maps surface Theorem~4.92 together with Corollaries~4.93--4.95, and they note that the Wilson/RG identification on $\mathcal A_{\mathrm{flow}}$ uses the flowed de-patching seam in Companion~I Section~III.\\
Lane~A bridge visibility & Packet~6 now surfaces the promoted theorem-facing finite-cap bridge 5.74A between Theorem~F.331 and Theorem~5.74. The positivity / unitality mechanism is no longer left implicit below the theorem-facing surface.\\
Lane~A compatibility seam & Public mapping surfaces Corollary~5.75 separately from Corollary~5.76 so bounded-state restriction compatibility is not conflated with the inductive-union passage.\\
Route~1 packet label & Packet~8 points to Core Theorem~IV.2 / Companion~I Theorem~III.18 for the same-scale Wilson return. The stale public label ``Theorem~3.17'' is removed.\\
Live weak-window certificate & Theorem~F.298 remains the sole live weak-window sufficiency certificate on the public Route~1 spine.\\
Endpoint hygiene & The core title, abstract, and Section~I scope language now match the vacuum-sector local-net endpoint exactly; qualitative faithful-Wilson universality remains separate from the openly $\rho$-indexed quantitative non-claim.\\
\bottomrule
\end{tabularx}
\end{center}

\section{Recommended first-pass reading order}

\begin{itemize}
\item For a handling editor or a referee who has not yet committed to the full proof load, start with the core paper only, especially Sections~1--2, then Sections~3--7, then the core appendices.
\item For a short expert attack of the live theorem route, start instead with the proof kernel and descend only to the proof homes it cites.
\item If the question is ultraviolet/public scope, one-shot entrance, same-scale Wilson return, or continuum-gap transport, go next to Companion~I.
\item If the question is how the sharp-local algebra is built, or whether finite-cap closure, bridge 5.74A, bounded-state restriction compatibility, and the inductive-union passage are explicit, go next to Companion~II.
\item If the question is reconstruction, non-triviality, faithful-Wilson universality, or the exact local-net endpoint, go next to Companion~III.
\item If the question is final sign-off, pass conditions, or blocker-closure status, consult the Phase-IX closure gate after the relevant proof home has been checked.
\end{itemize}

\section{Core theorem-home map}

\begin{center}
\small
\begin{tabularx}{\linewidth}{@{}L{2.3cm}Y Y@{}}
\toprule
\textbf{Core theorem range} & \textbf{What it certifies} & \textbf{Proof home}\\
\midrule
3.1--3.3 & Ultraviolet/public-scope gate & Companion~I\\
4.1--4.3 & Route~1 lattice-side gap and weak-window closure & Companion~I\\
5.1--5.12 & Lane~A construction chain & Companion~II\\
6.1--6.6 & QE3 seam and continuum vacuum-gap transport & Companion~I\\
7.1--7.10 & Endpoint packet & Companion~III\\
\bottomrule
\end{tabularx}
\end{center}

\section{Reserve-use note}

Keep this note off the initial submission unless an editor or referee explicitly asks for routing help. If requested, send it together with the synchronized \emph{Supplementary Referee Dossier} and \emph{Analytic Certification Dossier}. Add the proof kernel for a short technical attack on the live theorem route, and add the Phase-IX closure gate only if package-level closure or sign-off status is the issue.

\end{document}
