
\documentclass[11pt]{article}
\input{support/support_style}
\input{support/support_metadata}
\begin{document}

\SupportTitleBlock
  {JMP Supplementary Referee Dossier}
  {Reserve dossier synchronized to the Phase-IX-hardened core-plus-companions submission structure.}
  {\ReserveOnlyNote\ This dossier is for theorem-routing and proof-home requests only. It mirrors the live proof surface and its derived audit roots, but it adds no new theorems and should not be treated as the first-touch manuscript. Updated \SyncDate.}

\section{Current synchronized submission structure}

\begin{center}
\small
\begin{tabularx}{\linewidth}{@{}L{2.2cm}Y@{}}
\toprule
\textbf{Component} & \textbf{Role in the synchronized bundle}\\
\midrule
Core paper & States the exact theorem-level claim, public packet reduction, decisive seam nodes, and the assembled proof.\\
Companion I & Carries the ultraviolet/public-scope gate, Route~1 lattice-side burden, same-scale Wilson return, QE3 seam, and continuum vacuum-gap transport.\\
Companion II & Carries the full Lane~A sharp-local construction chain: Packet~4 front end, exact-dimension breadth, finite-truncation inverse control, finite-cap bridge 5.74A, finite-cap closure, bounded-state restriction compatibility, inductive-union passage, and bounded-base cyclicity.\\
Companion III & Carries the claim-facing endpoint packet: Euclidean OS dossier, Wightman--Haag--Kastler reconstruction, field correspondence, non-triviality, qualitative faithful-Wilson universality, and the exact local-net endpoint.\\
Proof kernel & Provides a compact expert-audit extraction of the load-bearing packet route and the import / exclusions boundary.\\
Phase-IX closure gate & Records the final pass conditions, theorem-node closure matrix, submission inventory, and sign-off checklist; it is an audit packet, not a proof home.\\
\bottomrule
\end{tabularx}
\end{center}

\section{Public theorem packets under the final bundle}

\small
\setlength{\LTleft}{0pt}
\setlength{\LTright}{0pt}
\begin{longtable}{@{}C{0.8cm}L{9.5cm}L{4.0cm}@{}}
\toprule
\textbf{Pkt} & \textbf{Theorem-facing content} & \textbf{Live proof home}\\
\midrule
\endfirsthead
\toprule
\textbf{Pkt} & \textbf{Theorem-facing content} & \textbf{Live proof home}\\
\midrule
\endhead
\bottomrule
\endfoot
1 & Theorem~N.20 and Corollary~N.21. Compact-simple A1 ultraviolet gate and public group-scope export. & Core Section~3 + Companion~I\\
2 & Proposition~F.3, with proof-local hardening by Theorem~F.317 and Corollary~F.318. One-shot entrance into the KP/Dobrushin basin at bounded physical scale. & Core Sections~3--4 + Companion~I\\
3 & Proposition~F.4, with proof-local culmination at Theorem~F.308. Tuned full fixed-lattice OS gap. & Core Section~4 + Companion~I\\
4 & Theorem~4.92 and Corollaries~4.93--4.95. Unique flowed continuum state, Wilson/RG identification on $\mathcal A_{\mathrm{flow}}$, tuned bounded positive-time base state, and dyadic reflected OS limits. & Core Sections~5--6 + Companion~II Appendix~A, with the flowed de-patching seam in Companion~I Section~III\\
5 & Theorem~L.8, Theorem~L.11, Theorem~5.39, Theorem~5.69, and Corollary~F.245. Exact-dimension breadth plus finite-truncation inverse / remainder control. & Core Section~5 + Companion~II\\
6 & Corollary~F.330A, Theorem~F.331, promoted bridge~5.74A, Theorem~5.74, Corollary~5.75, and Corollary~5.76. Finite mixed-family packaging, first mixed-correlator closure at finite cap, theorem-facing positive / unital bridge into 5.74, finite-cap sharp-local extension, bounded-state restriction compatibility, and then the full sharp-local inductive-union passage. & Core Sections~5--6 + Companion~II\\
7 & Core Theorem~V.13 / Source Theorem~5.77. Bounded-base cyclicity. & Core Section~5 + Companion~II\\
8 & Core Theorem~IV.2 (proof home: Companion~I Theorem~III.18), Theorems~F.211 and~F.212, Corollary~F.213, Lemma~F.214, Theorem~F.216, Corollary~F.5, and auxiliary certificate Theorem~F.298. Wilson-to-continuum transport and continuum vacuum gap, with F.298 as the sole live weak-window certificate. & Core Sections~4 and~6 + Companion~I\\
9 & Theorem~M.1, Theorem~M.3, Corollaries~M.4--M.5, and Theorem~M.6. OS/Wightman existence, field correspondence, Minkowski-gap transfer, and non-triviality. & Core Section~7 + Companion~III\\
10 & Theorem~O.2, Theorem~O.3, Corollary~O.4, Theorem~O.5, and Corollary~O.7. Qualitative faithful-Wilson universality, the $\rho$-indexed quantitative-status note, and the exact theorem-level local-net endpoint. & Core Section~7 + Companion~III\\
\end{longtable}

\section{Decisive seam nodes to keep visible}

\begin{center}
\small
\begin{tabularx}{\linewidth}{@{}L{3.1cm}Y Y@{}}
\toprule
\textbf{Seam / node} & \textbf{Why it matters now} & \textbf{Current live location}\\
\midrule
Core Theorem~IV.2 / Companion~I Theorem~III.18 & Single theorem-level same-scale Wilson return seam on the public Route~1 chain. & Core Section~4; proof in Companion~I Section~III\\
Theorem~F.331 & First mixed-channel finite-cap closure node feeding the promoted bridge. & Core Section~5 discussion; proof in Companion~II\\
Promoted bridge~5.74A & The theorem-facing finite-cap positivity / unitality bridge into Theorem~5.74. & Core Sections~5--6 discussion; proof in Companion~II\\
Corollary~5.75 & Bounded-state restriction compatibility node used on the QE3-facing Lane~A seam. & Core Sections~5--6 discussion; proof in Companion~II\\
Corollary~5.76 & Inductive-union passage from capwise sharp-local reconstruction to the full sharp-local algebra. & Core Section~5; proof in Companion~II\\
Theorem~5.77 & First bounded-base cyclicity export. & Core Section~5; proof in Companion~II\\
Lemma~F.214 & QE3 graph-core / density handoff. & Core Section~6; proof in Companion~I\\
Theorem~F.216 & Single transport node carrying the fixed-lattice lower bound to the continuum sharp-local Hilbert space. & Core Section~6; proof in Companion~I\\
Theorem~F.298 & Sole live weak-window sufficiency certificate on the Route~1 spine. & Core Sections~4 and~6 cross-reference; proof in Companion~I\\
\bottomrule
\end{tabularx}
\end{center}

\section{Non-load-bearing material under the split}

\begin{itemize}
\item Lane~B dense-core spectral-calculus reformulations.
\item Classical-family one-plaquette audits in Appendices~G--I and total-positivity tools in Appendix~J.
\item Sample scalar, tensor, and loop normalization channels retained in Appendix~L.
\item Historical fixed-$\beta$ threshold notes and older entrance-comparison material moved off the live Route~1 chain.
\item AQFT interpretive commentary downstream of the exact local-net endpoint.
\item Phase-VIII reports, issue trackers, disposition memos, and the Phase-IX closure gate packet: synchronized audit material only, not live theorem edges.
\item These reserve support papers themselves: organizational aids only, with no unique mathematical content.
\end{itemize}

\section{Suggested request-response protocol}

\begin{center}
\small
\begin{tabularx}{\linewidth}{@{}L{6.0cm}Y@{}}
\toprule
\textbf{If the request is...} & \textbf{Send...}\\
\midrule
``Please point me to the exact proof home for the gap route.'' & This dossier + the Referee Concordance and Reading Note + Companion~I. Add the proof kernel if the reader wants the shortest live route.\\
``Please identify the Lane~A construction path and tell me what is load-bearing.'' & This dossier + Companion~II.\\
``Please explain endpoint or universality claims and the faithful-$\rho$ scope note.'' & This dossier + Companion~III.\\
``Please explain how the theorem-facing analytic route is organized after final hardening.'' & This dossier + the Analytic Certification Dossier.\\
``Please show me the final sign-off / blocker-closure packet.'' & This dossier + \texttt{phase9\_closure\_gate.tex} or its compiled PDF.\\
\bottomrule
\end{tabularx}
\end{center}

\section{Reserve packet integrity note}

Revise this dossier again if theorem numbers, packet labels, component titles, or page counts change before submission. The reserve packet must always mirror the live bundle, not an outdated monolithic or pre-kernel baseline.

\end{document}
