\begin{thebibliography}{99}

\bibitem{OS1}
K.~Osterwalder and R.~Schrader,
\newblock \emph{Axioms for Euclidean Green\'s functions},
\newblock \emph{Communications in Mathematical Physics} \textbf{31} (1973).

\bibitem{OS2}
K.~Osterwalder and R.~Schrader,
\newblock \emph{Axioms for Euclidean Green\'s functions II},
\newblock \emph{Communications in Mathematical Physics} \textbf{42} (1975).

\bibitem{OSSeiler1978}
K.~Osterwalder and E.~Seiler,
\newblock \emph{Gauge field theories on a lattice},
\newblock \emph{Annals of Physics} \textbf{110} (1978).

\bibitem{Wilson1974}
K.~G.~Wilson,
\newblock \emph{Confinement of quarks},
\newblock \emph{Physical Review D} \textbf{10} (1974).

\bibitem{GrossWilczek1973}
D.~J.~Gross and F.~Wilczek,
\newblock \emph{Ultraviolet behavior of non-Abelian gauge theories},
\newblock \emph{Physical Review Letters} \textbf{30} (1973).

\bibitem{Politzer1973}
H.~D.~Politzer,
\newblock \emph{Reliable perturbative results for strong interactions?},
\newblock \emph{Physical Review Letters} \textbf{30} (1973).

\bibitem{Luscher2010}
M.~L\"uscher,
\newblock \emph{Properties and uses of the Wilson flow in lattice QCD},
\newblock \emph{Journal of High Energy Physics} \textbf{1008} (2010) 071.

\bibitem{Aronson1967}
D.~G.~Aronson,
\newblock \emph{Bounds for the fundamental solution of a parabolic equation},
\newblock \emph{Bulletin of the American Mathematical Society} \textbf{73} (1967).

\bibitem{Davies1989}
E.~B.~Davies,
\newblock \emph{Heat Kernels and Spectral Theory},
\newblock Cambridge University Press, 1989.

\bibitem{KoteckyPreiss1986}
R.~Koteck\'y and D.~Preiss,
\newblock \emph{Cluster expansion for abstract polymer models},
\newblock \emph{Communications in Mathematical Physics} \textbf{103} (1986) 491--498.

\bibitem{Brydges1986}
D.~C.~Brydges,
\newblock \emph{A short course on cluster expansions},
\newblock in \emph{Critical Phenomena, Random Systems, Gauge Theories} (Les Houches, Session XLIII, 1984),
  eds.~K.~Osterwalder and R.~Stora, North-Holland, 1986.

\bibitem{Dobrushin1968}
R.~L.~Dobrushin,
\newblock \emph{The description of a random field by means of conditional probabilities and conditions of its regularity},
\newblock \emph{Theory of Probability and its Applications} \textbf{13} (1968) 197--224.

\bibitem{Hornik2014}
K.~Hornik and B.~Gr\"un,
\newblock \emph{Amos-type bounds for modified Bessel function ratios},
\newblock \emph{J. Math. Anal. Appl.} \textbf{408}(1):91--101, 2013.

\bibitem{HornikGrun2024}
K.~Hornik and B.~Gr\"un,
\newblock \emph{Generalized Amos--type bounds for modified Bessel function ratios},
\newblock \emph{Mathematical Inequalities \& Applications} \textbf{27}(4) (2024), 775--787.

\bibitem{Amos1974}
D.~E.~Amos,
\newblock \emph{Computation of modified Bessel functions and their ratios},
\newblock \emph{Mathematics of Computation} \textbf{28}(125) (1974), 239--251.

\bibitem{Dehaye2011}
P.-O.~Dehaye,
\newblock On an identity due to Bump and Diaconis, and Tracy and Widom,
\newblock \emph{Canadian Mathematical Bulletin} \textbf{54}(2) (2011), 255--269.

\bibitem{BumpDiaconis2002}
D.~Bump and P.~Diaconis,
\newblock Toeplitz minors,
\newblock \emph{J. Combin. Theory Ser. A} \textbf{97}(2) (2002), 252--271.

\bibitem{Edrei1953}
A.~Edrei,
\newblock On the generating functions of totally positive sequences,
\newblock \emph{Transactions of the American Mathematical Society} \textbf{74} (1953), 367--383.

\bibitem{Karlin1968}
S.~Karlin,
\newblock \emph{Total Positivity},
\newblock Vol.~1, Stanford University Press, 1968.

\bibitem{Pinkus1996}
A.~Pinkus,
\newblock \emph{Totally Positive Matrices},
\newblock Cambridge University Press, 1996; reprinted with corrections, 2010.

\bibitem{PalesRadacsi2018}
Zs.~P\'ales and \'E.~Sz\'ekelyn\'en\'e Rad\'acsi,
\newblock \emph{A new characterization of convexity with respect to Chebyshev systems},
\newblock \emph{Journal of Mathematical Inequalities} \textbf{12}(3) (2018), 605--617.

\bibitem{Wasowicz2006}
Sz.~Wasowicz,
\newblock \emph{Some properties of generalized higher-order convexity},
\newblock \emph{Publ. Math. Debrecen} \textbf{68} (2006), no.~1--2, 171--182.

\bibitem{LuscherWeisz1985}
M.~L\"uscher and P.~Weisz,
\newblock \emph{On-shell improved lattice gauge theories},
\newblock \emph{Communications in Mathematical Physics} \textbf{97} (1985), 59--77.

\bibitem{Husung2023}
N.~Husung,
\newblock \emph{Logarithmic corrections to O($a$) and O($a^2$) effects in lattice QCD with Wilson or Ginsparg--Wilson quarks},
\newblock \emph{European Physical Journal C} \textbf{83} (2023), 142.

\bibitem{Sugiura1971}
S.~Sugiura,
\newblock \emph{Fourier series of smooth functions on compact Lie groups},
\newblock \emph{Osaka Journal of Mathematics} \textbf{8} (1971), 33--47.

\bibitem{JaffeWittenYM}
A.~Jaffe and E.~Witten,
\newblock \emph{Quantum Yang--Mills Theory},
\newblock in \emph{The Millennium Prize Problems}, Clay Mathematics Institute/American Mathematical Society, 2006.

\bibitem{DHR1}
S.~Doplicher, R.~Haag, and J.~E.~Roberts,
\newblock \emph{Local observables and particle statistics I},
\newblock \emph{Communications in Mathematical Physics} \textbf{23} (1971), 199--230.

\bibitem{DHR2}
S.~Doplicher, R.~Haag, and J.~E.~Roberts,
\newblock \emph{Local observables and particle statistics II},
\newblock \emph{Communications in Mathematical Physics} \textbf{35} (1974), 49--85.

\bibitem{DoplicherRoberts1990}
S.~Doplicher and J.~E.~Roberts,
\newblock \emph{Why there is a field algebra with a compact gauge group describing the superselection structure in particle physics},
\newblock \emph{Communications in Mathematical Physics} \textbf{131} (1990), 51--107.

\bibitem{StreaterWightman}
R.~F.~Streater and A.~S.~Wightman,
\newblock \emph{PCT, Spin and Statistics, and All That},
\newblock Princeton University Press, 2000.

\bibitem{Haag1996}
R.~Haag,
\newblock \emph{Local Quantum Physics},
\newblock 2nd ed., Springer, 1996.

\bibitem{BasuPollackRoy2006}
S.~Basu, R.~Pollack, and M.-F.~Roy,
\newblock \emph{Algorithms in Real Algebraic Geometry},
\newblock 2nd ed., Springer, 2006.

\end{thebibliography}
