\section{Compact Appendix C: standing quotient, tensor/skin discipline, and local closure}
\label{app:quotient}

This appendix records the quotient and local-closure results the body needs in order to treat all same-domain governance-relevant distinctions as tensor-determined rather than skin-dependent.

\begin{definition}[Tensor content and standing equivalence]
For an evaluated state $x$, let $\mathrm{Ten}(x)$ denote its total standing-relevant content at the fixed scope. Write
\[
x \sim y \quad :\Longleftrightarrow \quad \mathrm{Ten}(x)=\mathrm{Ten}(y).
\]
A skin-level variation is any variation that leaves $\mathrm{Ten}(x)$ unchanged.
\end{definition}

\begin{theorem}[Standing quotient uniqueness]
Any same-scope standing presentation compatible with the fixed kernel factors uniquely through the standing quotient $X/{\sim}$. There is no non-isomorphic same-scope standing state space carrying more governance-relevant structure than that quotient.
\end{theorem}

\begin{proof}
If two presented states induce the same standing-relevant consequences under all lawful same-scope tests, any attempt to keep them distinct requires privileged presentation or unwitnessed extra load. Conversely, every admissibility-relevant distinction must be witnessed by tensor content. Therefore the quotient by standing equivalence is the unique standing-bearing state space up to isomorphism.
\end{proof}

\begin{corollary}[Tensor determination and skin neutrality]
All same-domain standing-bearing classification factors through tensor content. Skin carries zero inferential authority.
\end{corollary}

\begin{proof}
If a skin-only distinction changed standing-bearing classification, then two tensor-equivalent states would receive different same-scope verdicts. That would contradict the quotient uniqueness theorem. Hence skin may repackage or display tensor content but cannot create new governance force.
\end{proof}

\begin{theorem}[Local closure / no stricter admissibility-preserving refinement]
There is no admissibility-preserving auxiliary classifier on the same fixed substrate that refines standing more finely than tensor content while preserving the original same-domain admissibility behavior.
\end{theorem}

\begin{proof}
Any such classifier must either distinguish tensor-equivalent states or remain constant on tensor classes. If it distinguishes tensor-equivalent states, it introduces a second standing-bearing layer beneath the quotient, contradicting standing-quotient uniqueness. If it remains constant on tensor classes, it collapses to tensor-determined bookkeeping and is not a stricter standing-bearing layer at all.
\end{proof}

\begin{corollary}[Code-predicate collapse bridge]
Any same-domain code predicate or auxiliary coding layer that is admissibility-preserving but not tensor-distinguishing is closure-inert bookkeeping. Any one that is tensor-distinguishing reopens hidden gate work and is excluded.
\end{corollary}
