\section{Required pass conditions at the final gate}\label{sec:p9-pass}

\begin{description}[leftmargin=2.9cm,style=nextline]
\item[Theorem-local closure (\checkmark)] Local dependency ledgers now sit at the critical core, Companion~I, Companion~II, and Companion~III nodes, and the proof-home tables plus packet docket identify exactly where each live theorem is proved and what consumes it next.

\item[No seam ambiguity (\checkmark)] The role split among 5.74, 5.75, 5.76, 5.77, F.213, F.214, and F.216 is synchronized in the core, the proof homes, the phase-freeze concordance appendices, and the proof kernel. The finite-cap bridge into 5.74 is theorem-facing.

\item[Quantifier discipline (\checkmark)] Capwise versus full-union claims, dyadic versus all-time transport, finite-cap graph-core approximation, and logarithmic-depth Wilson-return uniformity are all frozen in theorem-facing form on the live route.

\item[Imported background bounded (\checkmark)] The standard KP/Dobrushin and OS/Wightman inputs are boxed explicitly in the concordance and proof-kernel imports appendices, and no other mathematical outsourcing is claimed.

\item[Claim hygiene (\checkmark)] The title, abstract, main theorem section, endpoint section, proof kernel, and Companion~III all frame exactly the bounded-region local gauge-invariant sharp-local net and its vacuum-sector mass gap, while preserving the qualitative faithful-Wilson universality claim and the explicit quantitative non-claims.

\item[Independent auditability (\checkmark)] The proof kernel now exposes the packet route, seam details, import boundary, and exclusions boundary in a form that outside specialists can attack directly without reconstructing the proof from reserve notes.
\end{description}

\paragraph{Interpretation.}
At this gate the project is not claiming that outside referee validation has already happened. It is claiming the narrower and necessary internal condition: after the synchronized repairs of Phases~I--VIII, the packaged suite now exposes the theorem object, the proof homes, the import boundary, the seam roles, and the audit documents in a form that an outside expert can attack directly.
