\section{Submission package assembled at Phase~IX}\label{sec:p9-package}

\begin{description}[leftmargin=3.3cm,style=nextline]
\item[\texttt{core.tex} --- live] Clean submission root stating the theorem object, the ten-packet public spine, the exact endpoint, and the theorem-facing appendices.

\item[\texttt{companion1.tex} --- live] Proof home for the ultraviolet / Route~1 / QE3 transport chain, including the repaired seam theorem F.212 and the continuum-gap packet.

\item[\texttt{companion2.tex} --- live] Proof home for the Lane~A finite-cap closure chain, the state-construction ledger, and the theorem-facing positivity bridge into 5.74.

\item[\texttt{companion3.tex} --- live] Proof home for reconstruction, non-triviality, qualitative faithful-Wilson universality, and the exact local-net endpoint.

\item[\texttt{proofkernel.tex} --- derived audit] Optional expert-circulation kernel containing the load-bearing packet route, the imported-background appendix, the exclusions appendix, and the synchronized audit pointers.

\item[Phase~VIII verification dossier --- derived audit] The synchronized manuscript-side adversarial-verification reports, issue tracker, dispositions, and sign-off checklist retained at the repository root and in the core / kernel verification appendices.

\item[\texttt{phase9\_closure\_gate.tex} --- derived audit] Final technical-closure packet collecting the pass conditions, theorem-node closure matrix, package inventory, checklist, and closure memo.

\item[Reserve routing notes --- reserve] Retained routing or editorial material only, including the synchronized support roots for the analytic certification dossier, the referee concordance and reading note, and the supplementary referee dossier, together with the reserve referee-audit packet, the executive proof sketch, and supporting editorial notes. These files add no mathematics and are not required to verify any live theorem edge.
\end{description}

\paragraph{Clean-build rule.}
The packaged project remains configured for pdf\LaTeX{} / \texttt{latexmk} with no Bib\TeX{} step. The shared manual bibliography block in \texttt{shared/bibliography.tex} remains authoritative for all roots. The external-label include files stay synchronized so the core, companions, and kernel can be built independently on Overleaf.
