\section{Final sign-off checklist and decision rule}\label{sec:p9-checklist}

\begin{enumerate}[leftmargin=2.2em,label=\textup{\arabic*.}]
\item Every theorem on the public spine is attached to a single canonical proof home. \emph{Primary evidence:} Core Appendix~C and the companion proof-home guides. \hfill $\checkmark$

\item The role split among 5.74, 5.75, 5.76, 5.77, F.213, F.214, and F.216 is identical in the core, Companion~I, Companion~II, the proof kernel, and the reserve-routing notices. \emph{Primary evidence:} Core Sections~V--VI; companion notes; kernel Sections~V--VI. \hfill $\checkmark$

\item F.212 cites the correct nodes with no ambiguity. \emph{Primary evidence:} Companion~I theorem F.212; core Section~VI. \hfill $\checkmark$

\item The finite-cap positivity / unitality bridge is theorem-facing and cited directly by 5.74. \emph{Primary evidence:} Companion~II theorem-facing bridge notes and theorem~5.74; core Section~V. \hfill $\checkmark$

\item All fixed-cap, familywise, dyadic, and full-union distinctions are explicit. \emph{Primary evidence:} Core Sections~IV--VI; Companion~II capwise ledgers; kernel packet route. \hfill $\checkmark$

\item Imported standard results are isolated and declared only where used. \emph{Primary evidence:} Core Appendix~B; proof-kernel imported-background appendix. \hfill $\checkmark$

\item The title, abstract, theorem statement, and endpoint section match the actual theorem object exactly. \emph{Primary evidence:} Core front matter and Sections~I, VII; proof-kernel front matter. \hfill $\checkmark$

\item A specialist can audit the proof kernel without reserve materials. \emph{Primary evidence:} Proof-kernel root, reading guide, exclusions appendix, and the synchronized Phase~VIII / Phase~IX audit pointers. \hfill $\checkmark$

\item Every previous red-team issue has a manuscript-level disposition. \emph{Primary evidence:} The retained Phase~VIII tracker, disposition memo, sign-off checklist, and the synchronized verification appendices in the core and kernel. \hfill $\checkmark$
\end{enumerate}

\paragraph{Decision rule.}
All nine mandatory checklist items are now marked yes on the packaged suite. Therefore, conditional on the underlying mathematics being correct, the manuscript bundle has reached the internal technical-closure state targeted by the plan: the remaining barriers are outside validation, top-tier journal review, post-publication scrutiny, and the waiting-period realities attached to any millennium-level claim.
