\section{Final closure memo}\label{sec:p9-memo}

\paragraph{Blocker-by-blocker closure record.}

\paragraph{B1.}
The QE3 seam theorem F.212 no longer conflates 5.75 with 5.76. Its proof and theorem-local note now separate bounded-state restriction compatibility, finite-cap sharp-local OS structure, the inductive-union passage, and the density / graph-core handoff. The original closure-critical citation defect has therefore been removed at the proof home itself.

\paragraph{B2.}
The finite-cap bridge into 5.74 is now theorem-facing. The state-construction ledger and the local bridge note make positivity, unitality, bounded positive-time representatives, and the finite-cap OS mechanism explicit where 5.74 uses them. The earlier objection that the theorem-facing bridge looked weaker than the theorem it served is therefore closed.

\paragraph{B3.}
Packet~8 is no longer compressed in a way that forces the reader to infer hidden Lane~A dependence. The core packet map, the QE3 section, and the proof kernel all state directly that the dyadic-to-all-time transport packet consumes the repaired Lane~A seam nodes. The distributed-hint failure mode is therefore closed.

\paragraph{B4.}
The theorem numbering and routing surface are now frozen. The packet docket, proof-home tables, canonical numbering crosswalk, and synchronized phase-freeze appendix make it possible to answer, for every public-spine theorem, where it is proved, what it does, and what consumes it next. The numbering-friction blocker is therefore closed.

\paragraph{B5.}
The front matter and endpoint prose no longer invite a broader reading than the theorem supports. The title, abstract, main theorem section, proof kernel, and Companion~III now all state the bounded-region local gauge-invariant sharp-local net / vacuum-sector mass-gap endpoint with the qualitative faithful-Wilson claim and the explicit quantitative / nonlocal non-claims preserved. The framing blocker is therefore closed.

\paragraph{B6.}
The project now contains a standalone proof kernel exposing the live packet route, seam details, import boundary, exclusions boundary, and expert reading guide without requiring reserve dossiers. This does not replace later external audit, but it does close the internal blocker that previously forced specialists to reconstruct the proof route from multiple surfaces.

\paragraph{Remaining work after Phase~IX.}
Within the manuscript bundle, no further theorem-local closure repair is planned. The remaining steps are external: independent specialist reading, top-tier referee review, post-publication scrutiny, and the real-world waiting-period constraints attached to any millennium-level claim. Within that scope, the suite has reached an internal closure-ready state for external specialist review; external independent audit remains outstanding.
