\section{Phase-VIII internal track reports and issue ledger}\label{app:kernel-issue-log}

This appendix records the internal adversarial pass organized by the four specialist tracks of Appendix~\ref{app:kernel-redteam}. It is intentionally explicit about scope: these are manuscript-side red-team reports and dispositions, not a claim that independent external experts have already signed off. Their function is to force all later attacks onto the same frozen theorem surface.

\subsection*{Disposition summary}
\begin{center}
\small
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.08}
\begin{tabular}{@{}p{3.1cm}p{1.35cm}p{1.35cm}p{1.35cm}p{1.2cm}@{}}
\toprule
\textbf{Track} & \textbf{Issues logged} & \textbf{Rewritten} & \textbf{Rebutted} & \textbf{Open}\\
\midrule
RG / lattice / cluster expansion & 2 & 1 & 1 & 0\\
OS / reflection positivity / measure & 2 & 1 & 1 & 0\\
Operator / domain / reconstruction & 2 & 1 & 1 & 0\\
Endpoint / universality / local net & 2 & 1 & 1 & 0\\
\midrule
Total & 8 & 4 & 4 & 0\\
\bottomrule
\end{tabular}
\end{center}

\paragraph{Track 1 report: RG / lattice / cluster expansion.}
\emph{Prompt.} Attack only Packets~1--3 and the sole live weak-window certificate. Treat any regression from logarithmic-depth wording to fixed-depth wording, or any second downstream weak-window intake, as closure-critical.\par
\emph{Disposition.} One rewrite was made at the kernel front door so that the attack map itself now points directly to the logarithmic-depth Wilson-return theorem and the sole live weak-window certificate. A separate false-citation suspicion was rebutted from the already frozen DAG and Route~1 ledger.

\paragraph{Track 2 report: OS / reflection positivity / measure.}
\emph{Prompt.} Attack only the state-construction chain from the bounded Wilson base state through the finite-cap bridge and the inductive-union passage. Treat any attempt to read positivity through unconstructed representatives, or to collapse capwise and full-union statements, as closure-critical.\par
\emph{Disposition.} One rewrite was made to box the allowed use sites of the imported OS / uniqueness background. A stronger-gap suspicion at the finite-cap positivity seam was rebutted from the theorem-facing bridge and the existing Packet~6 text.

\paragraph{Track 3 report: operator / domain / reconstruction.}
\emph{Prompt.} Attack only the dyadic OS limit, the continuum-time upgrade, the density / graph-core handoff, and the vacuum-gap transport. Treat any hidden domain completion or direct lattice all-time shortcut as closure-critical.\par
\emph{Disposition.} One rewrite was made in Section~\ref{sec:qe3-transport} so the exact operator-domain checklist is stated inline. A separate suspicion that Corollary~5.75 was still being used as the inductive-union theorem was rebutted from the already repaired seam language.

\paragraph{Track 4 report: endpoint / universality / local net.}
\emph{Prompt.} Attack only the theorem-level endpoint. Treat any conflation of qualitative faithful-Wilson universality, the $\rho$-indexed quantitative status, effective-group descent, or nonlocal-sector exclusion as claim overstatement.\par
\emph{Disposition.} One rewrite was made in Section~\ref{sec:endpoint} and one synchronization note was added to the core concordance appendix so the endpoint non-claims appear as a formal audit checklist. A broader overclaim suspicion was rebutted from the already synchronized theorem text.

\subsection*{Final issue tracker}
\begin{description}[leftmargin=2.2em,style=nextline]
\item[RG-01 -- hidden quantifier shift.] Affected nodes: front matter of the kernel, Theorem~\ref{thm:wilson-return}, and Theorem~\ref{thm:weak-window-certificate}.\
Disposition: \emph{rewritten}. The expert reading guide was recast as the four Phase-VIII specialist tracks and now sends the RG attack directly to the logarithmic-depth Wilson-return theorem plus the sole live weak-window certificate. This prevents a first-pass audit from silently downgrading the theorem-facing uniformity or inventing a second weak-window intake.

\item[RG-02 -- false citation.] Affected nodes: Proposition~\ref{prop:packet-reduction}, Figure~\ref{fig:kernel-dag}, and Theorem~\ref{thm:weak-window-certificate}.\
Disposition: \emph{rebutted}. The suspicion that the public Route~1 spine still depends on additional weak-window placeholders is answered directly by the frozen DAG, the packet docket, and Theorem~\ref{thm:weak-window-certificate}. No live theorem after that certificate cites a different weak-window node.

\item[OS-01 -- missing implication.] Affected nodes: Appendix~\ref{app:kernel-imports}, Theorem~\ref{thm:continuum-time-os-upgrade}, Theorem~\ref{thm:euclidean-os-dossier}, and Theorem~\ref{thm:faithful-wilson-universality}.\
Disposition: \emph{rewritten}. Appendix~\ref{app:kernel-imports} now contains an explicit use-site matrix for the boxed standard imports and states the rule that an import may not be invoked earlier than the theorem node listed there. This makes the import boundary attackable theorem by theorem.

\item[OS-02 -- real mathematical gap.] Affected nodes: Theorem~\ref{thm:finite-cap-extension} and the Packet~6 seam discussion of Section~\ref{sec:laneA}.\
Disposition: \emph{rebutted}. The suspicion that finite-cap positivity relies on undeclared representatives is answered by the existing theorem-facing bridge and the Packet~6 prose: reflection positivity is read only through bounded positive-time representatives, and the inverse-flow replacement error tends to zero before the capwise OS theorem is invoked. No new mathematical premise was needed.

\item[OP-01 -- hidden domain argument.] Affected nodes: Theorem~\ref{thm:continuum-time-os-upgrade}, Lemma~\ref{lem:qe3-graph-core}, and Theorem~\ref{thm:continuum-gap-transport}.\
Disposition: \emph{rewritten}. Section~\ref{sec:qe3-transport} now carries an explicit operator-domain attack checklist stating the only allowed route: dyadic limits on $A_+$, Lane~A identification inside the sharp-local OS reconstruction, density plus capwise finite-graph-norm approximants, and finally semigroup contraction plus the boxed spectral input.

\item[OP-02 -- false citation.] Affected nodes: Theorem~\ref{thm:continuum-time-os-upgrade}, Corollary~\ref{cor:full-inductive-union}, and Companion-II Corollary~5.75.\
Disposition: \emph{rebutted}. The suspicion that the QE3 seam still treats Corollary~5.75 as the inductive-union theorem is blocked by the already repaired seam language: 5.75 is only bounded-state restriction compatibility, Theorem~\ref{thm:finite-cap-extension} supplies the capwise OS structure, and Corollary~\ref{cor:full-inductive-union} is the later inductive-union passage.

\item[EP-01 -- claim overstatement.] Affected nodes: Theorem~\ref{thm:faithful-wilson-universality}, Corollary~\ref{cor:rho-indexed-ledger}, Theorem~\ref{thm:exact-local-net-endpoint}, and the core concordance appendix.\
Disposition: \emph{rewritten}. Section~\ref{sec:endpoint} now includes a formal endpoint non-claim checklist, and the core concordance appendix records where the Phase-VIII verification pack lives. The qualitative universality claim, the $\rho$-indexed quantitative non-claim, and the exclusion of nonlocal sector data are now separate audit items.

\item[EP-02 -- claim overstatement.] Affected nodes: Theorem~\ref{thm:faithful-wilson-universality}, Corollary~\ref{cor:group-only-endpoint}, and Theorem~\ref{thm:main}.\
Disposition: \emph{rebutted}. The suspicion that the group-only endpoint suppresses the admissible-scheme / coherent-normalization qualifiers is answered directly by the theorem text already in Section~\ref{sec:endpoint}. The qualifiers remain present where the faithful-Wilson identification is stated, and the quantitative non-claim stays separated in Corollary~\ref{cor:rho-indexed-ledger}.
\end{description}

\paragraph{Phase-VIII closure status.}
No closure-critical issue remains open in this internal Phase-VIII pass, and no kill criterion of Appendix~\ref{app:kernel-redteam} fired. The remaining external step is genuine specialist review rather than any further internal theorem-local synchronization of the manuscript itself.
