\section{Phase-VIII adversarial-verification program, prompts, and kill criteria}\label{app:kernel-redteam}

This appendix records the manuscript-side Phase-VIII adversarial-verification program applied to the hardened proof surface. It does \emph{not} claim external independent sign-off. Its job is narrower and theorem-facing: freeze the specialist attack prompts, issue taxonomy, and kill criteria that any later audit should use when attacking the live packet route.

\subsection*{Verification tracks and written prompts}
\begin{center}
\small
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.08}
\begin{tabular}{@{}p{2.55cm}p{4.95cm}p{2.8cm}p{2.3cm}@{}}
\toprule
\textbf{Track} & \textbf{Written attack prompt} & \textbf{Primary nodes under attack} & \textbf{Hard pass condition}\\
\midrule
RG / lattice / cluster expansion & Attack only the ultraviolet/public-scope gate, one-shot entrance, same-scale Wilson return, fixed-lattice gap, and the sole live weak-window certificate. Check that no summary regresses from logarithmic-depth uniformity to fixed-depth wording and that no second weak-window input appears downstream. & Packets~1--3, IV.2, IV.4 & no hidden quantifier shift and no duplicate weak-window intake\\
OS / reflection positivity / measure & Attack the bounded-state convergence, finite-family packaging, mixed-correlator closure, theorem-facing finite-cap bridge, and capwise-to-full-state chain. Check that positivity is read only through bounded positive-time representatives and that the inductive-union step is not smuggling in extra structure. & Packets~4--7, especially V.8--V.13 & finite-cap state and positivity are theorem-local\\
Operator / domain / reconstruction & Attack the bounded dyadic OS limit, dyadic-to-all-$t$ upgrade, density / graph-core handoff, continuum gap transport, and later reconstruction nodes. Check that no hidden domain completion or unavailable uniformity is used. & Packet~8 and Packet~9 & no hidden domain argument or direct lattice all-time shortcut\\
Endpoint / universality / local net & Attack only the theorem-level endpoint. Check that qualitative faithful-Wilson universality, the $\rho$-indexed quantitative non-claim, effective-group descent, and the exclusion of nonlocal sector data stay separate everywhere. & Packet~10 and the endpoint clauses of Theorem~\ref{thm:main} & no theorem-facing prose overstates the proved object\\
\bottomrule
\end{tabular}
\end{center}

\subsection*{Issue protocol}
Every objection in Appendix~\ref{app:kernel-issue-log} is logged with five pieces of data: an issue ID, the theorem nodes affected, one objection type, one final disposition, and the manuscript-level reason the issue is closed. The permitted objection types are exactly the closure-plan categories: false citation, missing implication, hidden quantifier shift, hidden domain argument, claim overstatement, and real mathematical gap. The permitted final dispositions are equally frozen: \emph{rewritten}, \emph{rebutted}, or \emph{route changed}. In this Phase-VIII pass no issue required a route change. An issue is not closed merely because an editorial note explains the intended route; it is closed only when the live proof text itself or the frozen kernel verification pack makes the objection impossible to sustain.

\subsection*{Kill criteria}
The internal red-team pass was run against the following explicit route-redesign triggers. If any one had fired, incremental editing would have stopped and the proof route would have needed redesign rather than polishing.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.25em]
\item a seam theorem really needs a stronger premise than any earlier theorem-facing node actually states;
\item a limit passage needs a uniformity statement not available on the stated fixed observable, fixed cap, or theorem-local domain;
\item a positivity or OS step depends on representatives, states, or algebras not yet constructed at the theorem node where they are used;
\item an endpoint claim needs nonlocal sector data or a faithful-$\rho$-uniform quantitative comparison theorem that the manuscript does not prove.
\end{enumerate}
No trigger above fired in the internal Phase-VIII pass recorded in Appendix~\ref{app:kernel-issue-log}. The live theorem route therefore remains the same Packet~1--10 route frozen earlier; only the attack surface and the disposition record have been hardened.

\subsection*{Deliverables captured here}
The manuscript-side Phase-VIII deliverables are therefore:
\begin{itemize}
    \item the frozen four-track attack program and prompts in this appendix;
    \item the final issue tracker and track reports in Appendix~\ref{app:kernel-issue-log};
    \item the small live-text rewrites identified there, which are now synchronized in the kernel and the core concordance appendix.
\end{itemize}
External independent specialist sign-off remains a real-world review step rather than something manufactured inside the source tree.
