\documentclass[11pt]{article}
\usepackage{amsmath,amssymb}
\usepackage{geometry}
\geometry{margin=1in}

\title{Equivalence Completion for Neutrino Mixing and Oscillation Invariants}
\author{Amos Jay Maley}
\date{}

\begin{document}
\maketitle

\section*{Abstract}
We complete an equivalence map between flavor--mass bookkeeping and observable weak-transition bookkeeping for neutrino propagation in the oscillation regime. Parameters commonly treated as independently physical in a flavor-basis parameterization are shown to overcount tensor load once admissible redescription and regime transport are enforced. Only mass-squared differences and rephasing-invariant mixing combinations survive as invariant witnesses. The result is eliminative, invariant under admissible redescription, and introduces no new physics.

\section{Apparent Independence in Flavor--Mass Bookkeeping}
Let flavor states $\nu_\alpha$ be related to mass eigenstates $\nu_i$ by a unitary matrix $U$,
\begin{equation}
\nu_\alpha = \sum_i U_{\alpha i}\,\nu_i .
\end{equation}
In flavor--mass bookkeeping, one parameterizes $U$ by angles and phases and treats these parameters together with masses $\{m_i\}$ as independent physical inputs.

\section{Observable Transition Bookkeeping}
In the oscillation regime, transition amplitudes depend on interference between mass eigenstates. For baseline $L$ and energy $E$, the transition probability takes the form
\begin{equation}
P_{\alpha\to\beta}
=\sum_{i,j} U_{\alpha i}U_{\beta i}^*U_{\alpha j}^*U_{\beta j}
\exp\!\left(-i\,\frac{\Delta m_{ij}^2 L}{2E}\right),
\end{equation}
where
\begin{equation}
\Delta m_{ij}^2 \equiv m_i^2 - m_j^2 .
\end{equation}

\section{Admissible Redescription: Rephasing}
Consider admissible flavor and mass rephasings,
\begin{equation}
\nu_\alpha \rightarrow e^{i\phi_\alpha}\nu_\alpha,
\qquad
\nu_i \rightarrow e^{i\psi_i}\nu_i.
\end{equation}
These induce
\begin{equation}
U_{\alpha i} \rightarrow e^{i\phi_\alpha}U_{\alpha i}e^{-i\psi_i}.
\end{equation}
Under these admissible redescriptions, the quantities
\begin{equation}
U_{\alpha i}U_{\beta i}^*U_{\alpha j}^*U_{\beta j}
\end{equation}
are invariant, while many individual parameterization phases are not.

\section{Lemma: Invariant Witness Counting}
If a tensor load contains $n$ independent degrees of freedom, admissible redescription and regime transport must preserve $n$ independent invariant witnesses across all admissible skins describing the same regime. A parameter that can be varied without changing any invariant witness is redundancy and has no standing as an independent tensor degree.

\section{Failure of Independence}
Assume that the full parameterization degrees of freedom of $U$ (angles and phases) together with $\{m_i\}$ correspond to independent tensor degrees. Observable transition bookkeeping exposes only:
\begin{itemize}
\item mass-squared differences $\Delta m_{ij}^2$ (not absolute mass offsets), and
\item rephasing-invariant products $U_{\alpha i}U_{\beta i}^*U_{\alpha j}^*U_{\beta j}$.
\end{itemize}
No additional independent invariant witnesses exist. Preservation of the assumed independence would require hidden unwitnessed structure, loss of tensor load under transport, or representational privilege. Each constitutes standing failure.

\section{Forced Tensor Relation}
The neutrino oscillation tensor load is uniquely specified by the invariant set:
\begin{equation}
\boxed{\;\Delta m_{ij}^2 \equiv m_i^2 - m_j^2\;}
\end{equation}
together with the rephasing-invariant mixing factors
\begin{equation}
\boxed{\;U_{\alpha i}U_{\beta i}^*U_{\alpha j}^*U_{\beta j}\;}
\end{equation}
appearing in
\begin{equation}
\boxed{\;
P_{\alpha\to\beta}
=\sum_{i,j} U_{\alpha i}U_{\beta i}^*U_{\alpha j}^*U_{\beta j}
\exp\!\left(-i\,\frac{\Delta m_{ij}^2 L}{2E}\right)
\;}
\end{equation}
Any parameterization freedom in $U$ beyond these rephasing invariants is redundancy. Absolute mass offsets are not invariant witnesses in this skin.

\section{Corollaries}
\begin{itemize}
\item Rephasing-removable phases in $U$ have no standing as independent tensor degrees.
\item Any two parameter sets producing the same $\Delta m_{ij}^2$ and the same rephasing-invariant products are tensor-identical for oscillation phenomena.
\item Any framework asserting additional independently tunable observable transition degrees beyond $\Delta m^2$ and rephasing invariants violates standing unless it introduces forbidden tensor load.
\end{itemize}

\section*{Conclusion}
Equivalence completion collapses apparent freedom in neutrino mixing parameterizations to an invariant witness set. The result is eliminative, representation-invariant, and irreversible under admissible redescription.

\end{document}

