\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[margin=1in]{geometry}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}

\title{L1 --- Equivalence Completion (Paper 10):\\
Higgs Alignment $\Longleftrightarrow$ Absence of Tree-Level Flavor-Changing Neutral Currents}
\author{Amos Jay Maley}
\date{}

\begin{document}
\maketitle

\section*{0. Scope and Non-Negotiables}
This paper is eliminative. It introduces no new primitives, no new ontology, no new anchors, and no new tensor load.
All results are invariant under admissible redescription and must survive hostile review without patching.

\section*{1. Apparent Independence}
In unbroken electroweak bookkeeping, Higgs--fermion Yukawa couplings appear freely choosable subject only to gauge invariance.
In broken-phase bookkeeping, neutral currents are observed to be flavor-diagonal at tree level, while charged currents mix.
The absence of tree-level FCNCs is often treated as empirical or texture-dependent.

\section*{2. Admissibility Envelope}
Allowed redescriptions include gauge basis $\leftrightarrow$ mass basis transformations and equivalent parameterizations.
Standing is fail-closed: admissible redescription must not create or remove independent flavor degrees of freedom.
Closure forbids importing textures, symmetries, or additional fields to repair transport failures.

\section*{3. Cross-Skin Transport}
Yukawa structures in the unbroken skin determine both mass matrices and the basis of neutral currents after symmetry breaking.
Any misalignment between Yukawa couplings and mass eigenstates transports into off-diagonal neutral-current couplings.

\section*{4. Failure of Independence}
Assuming free Higgs--fermion misalignment generically yields tree-level FCNCs after transport.
Removing them requires new structure, violating closure.
Conversely, strict FCNC absence must transport back as a constraint on admissible Higgs alignment.
Hence independence fails.

\section*{5. Forced Tensor Relation}
\begin{theorem}[Higgs Alignment--FCNC Equivalence]
Under admissible redescription and with no new load,
gauge--Higgs coupling alignment in the unbroken electroweak skin is equivalent to the absence of tree-level flavor-changing neutral currents in the broken-phase skin.
Natural flavor conservation is therefore a transport-invariant tensor constraint.
\end{theorem}

\begin{corollary}[Parameter Collapse]
For each fermion charge sector, admissibility permits only a single Yukawa matrix up to admissible field redefinition.
\end{corollary}

\begin{corollary}[Closure Uniqueness]
Tree-level FCNCs are forbidden without adding new structure.
Natural flavor conservation is closure-unique.
\end{corollary}

\section*{6. Hostile Referee Pass}
All attempts to treat FCNC absence as empirical,
to tune away misalignment,
or to introduce extra structure fail under admissibility and closure.

\section*{7. Closure Statement}
The absence of tree-level FCNCs is not an additional assumption.
It is the broken-phase expression of admissible Higgs--fermion alignment.

\end{document}

