\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[margin=1in]{geometry}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}

\title{L1 --- Equivalence Completion (Paper 8):\\
Unitary Mixing Saturation under Admissible Redescription}
\author{Amos Jay Maley}
\date{}

\begin{document}
\maketitle

\section*{0. Scope and Non-Negotiables}
This paper is eliminative. It introduces no new primitives, no new ontology,
no new anchors, and no new tensor load.
All results are invariant under admissible redescription.

We work with a fixed fermion generation count and fixed chiral load.
No additional fermions, no additional Higgs multiplets,
and no compensating sectors are permitted.
All admissible freedom must survive cross-skin transport.

\section*{1. Apparent Freedom of Unitary Mixing}
In broken-phase bookkeeping,
fermion mixing appears encoded in arbitrary unitary matrices
relating interaction eigenstates to mass eigenstates.
This suggests a continuous freedom of mixing angles and phases,
treated as independent physical parameters.

In gauge-phase bookkeeping,
only representation content and gauge-invariant operators appear explicit,
and unitary rotations are treated as basis artifacts.
This creates an apparent asymmetry in where mixing data is located.

\section*{2. Admissibility Envelope}
Allowed redescriptions include:
\begin{itemize}
\item unitary field redefinitions preserving gauge-covariant kinetic terms,
\item basis changes within fixed fermion multiplets,
\item reparameterizations preserving invariant operator content.
\end{itemize}

Any purported degree of freedom that cannot be transported between skins
without importing new structure is inadmissible.

\section*{3. Transport of Mixing Data}
Mixing matrices arise from the diagonalization of admissible Yukawa operators.
They therefore encode no independent structure beyond
the existence and form of those operators.

Transport from the broken-phase skin to the gauge-phase skin
erases explicit mixing matrices,
retaining only operator-existence conditions.
Conversely, any mixing appearing in the broken phase
must descend from admissible operator structure in the gauge phase.

\section*{4. Saturation of Unitary Freedom}
Assume arbitrary independent unitary mixing data in the broken phase.
Transport to the gauge phase.

If such data does not correspond to admissible operator structure,
it cannot be represented without:
(i) enlarging the fermion load,
(ii) introducing compensating multiplets, or
(iii) adding non-gauge-invariant terms.
Each option is forbidden.

Therefore, all admissible unitary mixing freedom
is exhausted by basis choice and operator diagonalization.
No residual independent degrees of freedom survive transport.

\section*{5. Core Result}
\begin{theorem}[Unitary Mixing Saturation under Admissible Transport]
Fix the fermion generation count and chiral load.
Under admissible redescription and under the global constraints
(no new load, no patches),
all admissible unitary mixing freedom is saturated by
basis reparameterization and Yukawa operator diagonalization.

No additional independent unitary mixing parameters exist
with standing across skins.
\end{theorem}

\begin{corollary}[Phase Exhaustion]
All admissible phases are either removable by redefinition
or fixed by operator structure.
No physical phases remain beyond those already encoded
in admissible Yukawa data.
\end{corollary}

\begin{corollary}[Skin Illusion of Mixing Freedom]
The appearance of free unitary mixing parameters
is a bookkeeping artifact of the broken-phase skin.
Cross-skin admissibility collapses this illusion.
\end{corollary}

\section*{6. Closure Statement}
Unitary mixing does not constitute independent physical structure.
It is fully exhausted by admissible operator content
and basis choice under fixed load.
No additional degrees of freedom survive admissible transport.

\end{document}

