\documentclass[11pt]{article}
\usepackage{amsmath,amssymb}
\usepackage{geometry}
\geometry{margin=1in}

\title{Equivalence Completion Between Yukawa and Mass Bookkeeping}
\author{Amos Jay Maley}
\date{}

\begin{document}
\maketitle

\section*{Abstract}
We complete an equivalence map between electroweak Higgs--Yukawa bookkeeping and low-energy mass-based bookkeeping. Parameters commonly treated as independent in ultraviolet descriptions are shown to overcount tensor load once admissible redescription and regime transport are enforced. The fermion sector admits a single invariant witness per species. The result is eliminative, invariant under admissible redescription, and introduces no new physics.

\section{Apparent Independence in Higgs--Yukawa Bookkeeping}
In electroweak bookkeeping with a scalar doublet, fermion masses arise from Yukawa interactions
\begin{equation}
\mathcal{L}_Y = -y_f\,\bar{\psi}_{f,L}\,\phi\,\psi_{f,R} + \text{h.c.}
\end{equation}
After symmetry breaking, the fermion mass is
\begin{equation}
m_f = \frac{y_f v}{\sqrt{2}} ,
\end{equation}
where $y_f$ and $v$ are treated as independent inputs in this skin.

\section{Admissible Low-Energy Bookkeeping}
An admissible low-energy description of the same fermion sector contains massive fermion fields with mass parameter $m_f$. Interaction strengths, thresholds, and propagators depend on $m_f$ and gauge couplings. No independent parameter corresponding to $y_f$ appears.

\section{Lemma 1: Cross-Skin Transport}
Admissible transport from the Higgs--Yukawa skin to the low-energy massive-fermion skin identifies
\begin{equation}
m_f \;\leftrightarrow\; \frac{y_f v}{\sqrt{2}} .
\end{equation}
All fermion-sector amplitudes in the low-energy skin depend on $m_f$ alone.

\section{Lemma 2: Invariant Witness Counting}
If a tensor load contains $n$ independent degrees of freedom, admissible redescription and regime transport must preserve $n$ independent invariant witnesses across all admissible skins describing the same regime. A skin exposing fewer invariant witnesses implies redundancy in higher-dimensional parameterizations.

\section{Failure of Independence}
Assume $(y_f, v)$ are independent tensor degrees for fermion threshold and interaction content. By Lemma~2, two invariant witnesses must survive admissible transport. The low-energy skin exposes only one invariant witness, $m_f$. Preservation of independence would require loss of tensor load, hidden unwitnessed structure, or representational privilege. Each constitutes standing failure.

\section{Forced Tensor Relation}
The admissible fermion-sector tensor load is uniquely specified by
\begin{equation}
\boxed{\;m_f \equiv \frac{y_f v}{\sqrt{2}}\;}
\end{equation}
for each fermion species $f$. The Yukawa parameter $y_f$ is not independently admissible as a tensor degree for fermion threshold or interaction content once $m_f$ is fixed.

\section{Corollaries}
\begin{itemize}
\item The fermion sector admits a one-dimensional tensor load per species.
\item Higgs--Yukawa and mass-based descriptions are tensor-identical after redundancy elimination.
\item Any framework treating $(y_f, v)$ as independently physical for low-energy fermion content overcounts tensor degrees and violates standing.
\end{itemize}

\section*{Conclusion}
Equivalence completion enforces collapse of apparent freedom between Yukawa and mass bookkeeping. The result is eliminative, representation-invariant, and irreversible under admissible redescription.

\end{document}

