\maketitle

\begin{tcolorbox}[title={Main endpoint theorem (Fefferman (B), periodic case)}, colback=blue!2!white, colframe=blue!55!black]
\textbf{Classical endpoint.}
Let $\nu>0$ and let $u_0\in C^\infty(\T^3;\R^3)$ satisfy $\nabla\cdot u_0=0$.
Then there exists a unique smooth periodic Navier--Stokes solution pair $(u,p)$ on
$\T^3\times[0,\infty)$ satisfying
\[
\partial_t u + (u\cdot\nabla)u + \nabla p = \nu\Delta u,
\qquad \nabla\cdot u = 0,
\qquad u|_{t=0}=u_0,
\]
with the fixed mean-zero pressure gauge.
This classical statement is proved below first as Corollary~\ref{cor:official-periodic-structural-corollary} and then restated as Theorem~\ref{thm:official-periodic-pde-theorem}, making the claim type and the official PDE restatement explicit in that order.
\end{tcolorbox}

\paragraph{Proof mechanism.}
Part~I isolates the common analytic obstruction but does not close it by a new continuation estimate or by the missing analytic bridge inequality. The standing/intelligibility burden used later is now carried manuscript-locally by the fixed-scope packet ST1--ST3 in Part~II and the realized-lineage packet ST4--ST5 in Part~III. Part~II now also proves the future-behavior quotient / factorization / history-factorization / ATS packet theorem-locally, so same-scope admissibility cannot depend on path, order, or representative choice and no skin-level selector can become a hidden second gate. Phase~5 then localizes the actual Navier--Stokes observables used on the live route: passage among velocity / vorticity / strain / pressure / frequency presentations is skin-level, metric divergences, critical norms, and BKM-type quantities are licensed bookkeeping, and they become load-bearing only as quotient-visible witness bookkeeping subordinate to the already fixed horizon gate. Part~III now binds the admitted carrier seed to the full realized maximal lineage and proves that admissibility on that lineage is global rather than time-indexed, so the sentence "admissible before $T_*$, non-admissible at $T_*$" is theorem-locally ill-typed as a same-scope proposal. The governing thesis is narrower and more exact: once the official periodic classical scope is fixed and the realized maximal lineage is treated as one same-scope determination, any purported finite-horizon failure has only one licit same-scope endpoint status and two complementary non-licit proposal statuses. Its theorem-local proposal statuses are now explicit: a standing-positive admissible in-scope carrier witness, terminal standing failure, or an illicit same-scope gate / scope move. The standing-positive witness branch is exhausted and forced into a finite excluded branch family on the unique admissible interior, while the standing-failure and illicit branches are already collapsed manuscript-locally by standing--admissibility equivalence, standing conservation, irreversibility of representational commitment, factorization / no-path dependence, and the explicit realized-lineage status trichotomy of Part~III. Since no third licit same-scope endpoint status exists, the official periodic theorem follows.

\begin{tcolorbox}[title={Claim type and method class}, colback=green!2!white, colframe=green!45!black]
\textbf{Claim type and method class.}
This paper proves Fefferman's periodic statement~(B) by structural elimination of admissible singularity mechanisms, not by constructing solutions or deriving a new continuation estimate. Its endpoint is a \emph{same-scope closure-induced impossibility theorem}: under the forced admissibility regime established in Parts~I--III, finite-horizon breakdown has no same-scope completion --- neither as a standing-positive admissible realization nor as a standing-failure / illicit scope-change endpoint.

\medskip
\textbf{What the claim class does \emph{not} say.}
No sentence below should be read as asserting that admissibility by itself generates the missing analytic bridge inequality, a new coercive estimate, or a new continuation criterion. The theorem claimed here is only that, within the official periodic classical regime and its fixed same-scope continuation question, any purported finite-horizon failure has no licit same-scope status.

\medskip
\textbf{Structural route.}
\begin{enumerate}[leftmargin=1.8em, itemsep=0.15em, topsep=0.15em]
\item \textbf{Primitive structural forcing:} the fixed periodic problem admits the unique admissible interior by the structural packet \StructuralPacketRef{} together with the bridge packet culminating in Corollary~\ref{cor:periodic-unique-admissible-interior}.
\item \textbf{Carrier identification:} the standard periodic Navier--Stokes carrier is exactly that unique admissible interior by Theorem~\ref{thm:periodic-carrier-unique-interior}.
\item \textbf{Classical endpoint by local transfer and theorem-local endpoint-status collapse:} the official periodic theorem is obtained by the transfer cascade isolated in Theorem~\ref{thm:primitive-to-classical-transfer-cascade} together with the realized-lineage endpoint-status trichotomy / collapse of Part~III, then restated as Theorem~\ref{thm:official-periodic-pde-theorem}.
\end{enumerate}
\end{tcolorbox}

\paragraph{Official problem alignment and method-neutral evaluation frame.}
The endpoint theorem is a direct restatement of Fefferman's periodic statement~(B) for the three-dimensional incompressible Navier--Stokes equations on $\T^3$ \cite{fefferman-navierstokes-problem}. The Millennium Prize rules and the official Navier--Stokes problem statement impose no restriction on method class: a qualifying solution is judged by whether it establishes one of the official statements in a qualifying publication that survives public mathematical examination \cite{cmi-millennium-rules}. Accordingly, the present manuscript is evaluated on theorem-local adequacy for the full official periodic data class, not on whether it follows a continuation-estimate template or any other preferred proof style.

\paragraph{Primitive dependency declaration and load-bearing source freeze.}
The live proof chain for the present submission is frozen to the theorem-local material in the body of this manuscript, the fixed-scope exhaustion core of Appendix~A, the periodic local realization packet of Appendix~B, the compressed analytic atlas support of Appendix~E for Part~I, and stable public periodic Navier--Stokes local theory only to the extent a standard fact is named theorem-locally and not reproved in-body. Official problem alignment sources remain alignment only: they name the target theorem and the Clay publication rules but do not carry mathematical proof burden. Within that freeze, the only nonclassical load-bearing premises used below are the manuscript-local structural packet \StructuralPacketRef{}, the fixed-scope standing/intelligibility packet ST1--ST3 proved in Part~II, the realized-lineage standing/intelligibility packet ST4--ST5 proved in Part~III, and the fixed-scope exhaustion core proved in Appendix~A; the only analytic realization inputs used by Part~III are the periodic local lemmas proved in Appendix~B, while Part~I's compressed route survey depends only on the in-PDF analytic atlas of Appendix~E. No companion standing/intelligibility manuscript, corpus composite, dossier, theorem index, external validation report, slide deck, or privately circulated note is cited on the live proof chain. If a later phase of hardening chooses not to re-prove a standard local periodic fact in-body, it may invoke only a stable public PDE source theorem-locally; no private corpus text is an admissible substitute. Appendix~\ref{sec:internal-ledger}, especially the Phase-0 governance note in Appendix~\ref{sec:phase0-source-freeze}, mirrors this source freeze and records which supporting corpus papers are internalization targets, provenance only, or quarantined from the present submission.

\paragraph{No hidden endgame premises.}
All standing, admissibility, scope-fixity, quotient, and lineage premises used by the endgame are established within this manuscript, its load-bearing appendices, or stable public periodic PDE facts named theorem-locally exactly where they are used. No off-manuscript corpus theorem, external criterion, or companion-paper slogan is allowed to enter the live route to the official theorem.

\paragraph{Corpus governance and compatibility note.}
For this submission, corpus texts that are post-closure classificatory or that appear to undercut the closure route are not treated as premises. In particular, the paper \emph{Navier--Stokes Regularity as Fixation Persistence} is not imported by title into the live theorem chain. The only compatibility statement needed from that direction is now proved locally by Proposition~\ref{prop:boundary-licensing-same-scope-compatibility} together with Propositions~\ref{prop:metric-divergence-skin-non-authority} and \ref{prop:quotient-visible-witness-vs-illicit-metric-gate}: boundary licensing does not generate a new coercive estimate, while same-scope admissibility still governs which singularity representations are licit inside the official classical periodic scope. The external title therefore remains provenance / contrast only, and the later mirror / post-closure declarations remain excluded from the live theorem chain as proof sources.

\paragraph{What this paper does not attempt.}
This paper does not introduce a new a priori bound on the vortex-stretching channel, a weak-to-strong estimate program, or a constructive continuation scheme for large-data solutions. Part~I isolates the shared analytic wall; Proposition~\ref{prop:partIII-transport-only}, Proposition~\ref{prop:no-additional-pde-side-criterion}, and Theorem~\ref{thm:transfer-no-new-content} then make the Part~III role explicit: transport and faithful realization of an already certified structural theorem, with no new same-scope continuation criterion and no off-manuscript theorem on the live dependency chain.

\paragraph{Submission thesis (same-scope only).}
The submission thesis is the narrow one required by the official periodic classical problem. It is not that admissibility replaces periodic Navier--Stokes analysis in general, and it is not that admissibility alone produces global coercive control. It is that, once the official torus carrier, datum class, gauge, lawful-redescription class, and same-scope continuation question are fixed, any purported finite-horizon endpoint proposal for that exact problem has only three theorem-local proposal statuses: standing-positive admissible in-scope witness, terminal standing failure, or illicit same-scope gate / scope move. The last two are already collapsed locally in the manuscript, and the first is then exhausted and eliminated.

\begin{abstract}
We prove Fefferman's periodic statement~(B) for the three-dimensional incompressible Navier--Stokes equations on $\T^3$. The argument is not a constructive continuation proof and does not introduce a new a priori estimate. Instead, it is a closure-induced impossibility theorem.

Part~II isolates the unique admissible interior of the fixed periodic problem, proves the fixed-scope standing/intelligibility packet ST1--ST3 locally, and identifies the standard periodic Navier--Stokes carrier with that interior. Part~III constructs the local classical realization map, proves that the realized local class is exactly the full official local classical class, fixes the realized maximal classical lineage as one same-scope determination rather than a sequence of independently reclassified time slices, adds a carrier-to-lineage binding theorem and a no-admissibility-dynamics theorem specialized to realized periodic lineages, packages the resulting realized-lineage conservation/irreversibility consequences as ST4--ST5, and states the realized-lineage endpoint-status trichotomy and collapse explicitly.

The paper does not claim that admissibility itself supplies the missing analytic bridge inequality or a new continuation estimate. The claim is narrower: any hypothetical finite-time endpoint for the official periodic classical problem has only three theorem-local proposal statuses. It is either represented by a standing-positive admissible carrier witness, or it is terminal standing failure, or it is an illicit same-scope gate / scope move. The standing-positive branch yields a carrier-side horizon discriminator and, by same-scope witness exhaustion and branch forcing, a typed singular candidate lying in a finite excluded branch family. The standing-failure and illicit branches are not neutral exterior remainders; they are collapsed locally by the standing/intelligibility packet, factorization / no-path dependence, and the realized-lineage status trichotomy. Since no third licit same-scope endpoint status exists, the official periodic theorem follows for every smooth divergence-free datum.
\end{abstract}

\paragraph{Notation and scope conventions.}
Throughout, $\T^3:=\R^3/\mathbb{Z}^3$ and $\nu>0$ is fixed unless explicitly stated otherwise. The official periodic data class is denoted by $\mathcal D_{\mathrm{off}}(\T^3,\nu)$, the certified carrier-side admissible interior by $\mathcal I_{\mathrm{car}}(\T^3,\nu)$, the realization map by $\mathcal R_{\mathrm{NS}}(x)=(u_x,p_x)$, and $T_*(x)$ denotes the maximal classical realization time of a carrier state $x$. The glossary below records the remaining structural terms used in the front matter.

\paragraph{Same-object convention on the live chain.}
Beginning in Part~III, and already for the reader's first-page audit, the realized periodic Navier--Stokes lineage is treated as a single same-scope determination whose identity is fixed by the already-declared continuation interface and lawful-redescription class; see Definition~\ref{def:realized-lineage-same-object-convention} and Proposition~\ref{prop:partIII-same-continuation-notion}. The pre-horizon slices are therefore presentations of one realized lineage, not a family of independently reclassified admissibility states.

\paragraph{Live endgame spine (and only live route).}
The official theorem is obtained only through the explicit chain 19C--19F (PDE-native admissibility on the maximal classical interval) $\to$ 20B (carrier-to-lineage binding and no new same-scope classical discriminator) $\to$ ST4/ST5 (standing conservation and commitment persistence on the realized lineage) $\to$ 20C (endpoint-status trichotomy / collapse) $\to$ 21.x (branch elimination and official restatement). No alternate hidden route, off-manuscript companion theorem, or background corpus declaration carries the endpoint.

\paragraph{Bridge-patch live dependency chain.}
For the specific 12F / 12G / P4 seam, the only live periodic route is theorem-local and one-directional: 12F remains a live bridge premise, but only in the modest role of fixed-periodic scope-fixity / boundary-signature closure; 12G then applies P4 at that fixed scope and is the first local node where the no-second-gate consequence is obtained; 13K carries the resulting no-new-criterion consequence into the carrier packet; 20.5B and 20B transport that same consequence onto the realized classical layer; ST2--ST3 and 20C.1 transport the same fixed-scope packet into standing and endpoint-status language; and 20C consumes those carried channels in the realized-lineage trichotomy / collapse. Appendix~\ref{sec:bridge-patch-phase5-visibility-audit} audits this chain node by node and Appendix~\ref{sec:bridge-patch-phase6-lexical-audit} records the lexical / referee-pass cleanup. This chain is the only route by which the official theorem is obtained.

\section*{Front-of-paper roadmap, theorem map, glossary, denial map, and proof spine}
\addcontentsline{toc}{section}{Front-of-paper roadmap, theorem map, glossary, denial map, and proof spine}
For ease of verification, the boxes below collect the proof architecture in four compact views: the burden carried by each load-bearing node, the relation between the manuscript's structural language and ordinary periodic PDE language, the compressed proof spine, and the theorem-local denial targets for the standard objections. They expand the single live route just declared above and do not add a second path to the official theorem.

\begin{tcolorbox}[title={Referee roadmap: load-bearing nodes, burdens, and endpoint gains}, colback=blue!2!white, colframe=blue!55!black, boxsep=1pt, left=2pt, right=2pt, top=2pt, bottom=2pt]
\footnotesize
\renewcommand{\arraystretch}{1.10}
\setlength{\tabcolsep}{3.5pt}
\begin{tabularx}{\textwidth}{@{}L{0.23\textwidth}L{0.35\textwidth}Y@{}}
\toprule
\textbf{Load-bearing node} & \textbf{Burden carried here} & \textbf{What the endpoint gains if this node stands}\\
\midrule
Primitive packet + periodic bridge & Fix the unique admissible interior at fixed periodic scope, with live admissibility and the bridge antecedents proved theorem-locally before any carrier specialization. & The proof starts from one admitted same-scope regime, not from multiple rival periodic starting points or a bridge packet that is merely gestured at.\\
Finite same-scope typed classification & Classify and eliminate the finite typed family of standing-positive same-scope continuation candidate determinations on the fixed carrier before any broader PDE-totality claim is invoked. & No standing-positive same-scope rival carried by the typed packet survives outside the explicit elimination chain.\\
Carrier identification + burden closure & Identify the standard periodic carrier with the unique admissible interior and close the same-scope burden before Part~III. & Classical realization cannot reopen primitive admissibility or add a second same-scope interior.\\
Standing quotient + history-factorization + ATS roles & Fix same-scope identity by the future-behavior quotient, force every standing-relevant discriminator to factor through that quotient, rule out path-dependent same-scope admissibility, and strip standing authority from skin-level representative choices. & A hostile reader can no longer keep a same-scope blow-up alive by path/order dependence, representative-only diagnostics, or a hidden selector living in bookkeeping skin.\\
Transfer entry + completeness & Admit every official datum, identify the realized local class with the full official local classical class, and keep the same continuation notion fixed earlier. & The official Fefferman~(B) data class is fully covered, with no hidden prefilter, hidden subclass, or silent Part~III redefinition of continuation.\\
\bottomrule
\end{tabularx}
\end{tcolorbox}

\begin{tcolorbox}[title={Referee roadmap: load-bearing nodes, burdens, and endpoint gains (continued)}, colback=blue!2!white, colframe=blue!55!black, boxsep=1pt, left=2pt, right=2pt, top=2pt, bottom=2pt]
\footnotesize
\renewcommand{\arraystretch}{1.10}
\setlength{\tabcolsep}{3.5pt}
\begin{tabularx}{\textwidth}{@{}L{0.23\textwidth}L{0.35\textwidth}Y@{}}
\toprule
\textbf{Load-bearing node} & \textbf{Burden carried here} & \textbf{What the endpoint gains if this node stands}\\
\midrule
Transfer no-new-criterion + detectability & Prove that realization adds no new standing-positive same-scope continuation content on the live route and that finite-time breakdown is already carrier-visible. & Any classical finite-time breakdown is already a carrier-side witness rather than a new PDE-side continuation gate.\\
Standing/intelligibility packet ST1--ST5 & Internalize fixed reference, domain closure, lawful-redescription invariance, standing--admissibility equivalence, no standing-neutral drift, and no rollback of representational commitment in manuscript-local periodic language. & A hostile appeal to ``outside admissible representability'' must now confront named local theorems rather than an off-manuscript escape.\\
Realized-lineage status trichotomy / no-third-status collapse & State explicitly that any same-scope finite-horizon endpoint proposal is either a standing-positive admissible carrier witness, terminal standing failure, or an illicit same-scope gate / scope move, and that only the witness branch remains as a licit same-scope endpoint status. & ``Outside admissible representability'' and time-indexed admissibility drift become named collapsed proposal branches inside the proof rather than neutral external remainders.\\
Witness exhaustion + extraction & Exhaust every standing-positive same-scope breakdown witness entering the live endgame by the horizon discriminator and its induced branch data, then extract a typed singular candidate. & The branch-forcing machinery acts on the standing-positive witness class that actually enters the live endgame, not on a chosen encoding.\\
Branch forcing + branch elimination & Force any standing-positive breakdown witness into a nonempty forbidden branch set and exclude each branch. & No standing-positive singular image survives on the carrier already identified with the unique admissible interior.\\
Endpoint compression + official restatement & Transport the no-singular-image theorem into the official periodic theorem. & The final page-1 statement is Fefferman~(B) itself, not a merely structural surrogate.\\
\bottomrule
\end{tabularx}
\end{tcolorbox}

\begin{tcolorbox}[title={Theorem map for a first audit pass}, colback=blue!2!white, colframe=blue!55!black, boxsep=1pt, left=2pt, right=2pt, top=2pt, bottom=2pt]
\scriptsize
\renewcommand{\arraystretch}{1.08}
\setlength{\tabcolsep}{3pt}
\begin{tabularx}{\textwidth}{@{}L{0.28\textwidth}L{0.32\textwidth}Y@{}}
\toprule
\textbf{Question to check} & \textbf{Start here} & \textbf{What those labels settle}\\
\midrule
Which official problem is being answered, and what proof class is claimed? & Main endpoint theorem box on page~1, the Claim type and method class box, the Official problem alignment paragraph, and Theorem~\ref{thm:official-periodic-pde-theorem} & The endpoint is Fefferman's periodic statement~(B), and the proof is framed as a closure-induced impossibility theorem rather than as a constructive PDE continuation argument.\\
What exact classical object is being trapped by the closure route? & Definition~\ref{def:realized-lineage-same-object-convention}; Proposition~\ref{prop:partIII-same-continuation-notion}; the Same-object convention paragraph on page~1 & The realized maximal classical periodic solution is treated as one same-scope determination with one continuation question, not as a sequence of freshly reclassified admissibility states indexed by time slices.\\
Where is carrier identification transferred from the admitted carrier to the full realized lineage, and where is time-indexed admissibility blocked? & Theorems~\ref{thm:carrier-to-lineage-binding} and \ref{thm:no-admissibility-dynamics-realized-lineages}; Proposition~\ref{prop:standing-commitment-inheritance-realized-lineages}; Theorem~\ref{thm:st4-standing-conservation-realized-lineages} and Proposition~\ref{prop:st5-irreversibility-representational-commitment} & The admitted carrier seed, its realized maximal classical evolution, and the fixed continuation question are now bound into one standing-bearing same-scope determination, so admissibility cannot vary by time, restart stage, or horizon proximity along that lineage.\\
Where is admissibility derived directly from the maximal classical solution rather than imposed from outside? & Theorem~\ref{thm:pde-native-admissibility-maximal-interval}; Theorem~\ref{thm:restart-consistency-same-object-persistence}; Corollary~\ref{cor:pre-horizon-slice-reentry}; Lemma~\ref{lem:finite-horizon-witness} & The minimum fixed-reference / same-object / pre-horizon witness content used later is forced directly by standard local periodic theory on $[0,T_*(x))$, and any finite-horizon failure is already witnessed before the horizon.\\
Where are no path-dependent admissibility and no skin-authority proved locally? & Theorems~\ref{thm:standing-quotient-future-behavior}, \ref{thm:factorization-discipline-same-scope}, \ref{thm:history-factorization-no-path-dependent-admissibility}, and \ref{thm:ats-role-minimality-no-fourth-role}; Corollary~\ref{cor:skin-non-authority-representative-diagnostics}; Proposition~\ref{prop:periodic-carrier-interface-quotient-history} & Same-scope identity is fixed at the quotient level, every standing-relevant discriminator must factor through that quotient, path/order dependence is not available inside one standing class, and representative-only skin cannot become a hidden second gate.\\
Where are metric divergence, vorticity/pressure roles, and fixation-language compatibility localized? & Table~\ref{tab:periodic-ns-role-localization}; Definition~\ref{def:quotient-visible-witness-bookkeeping}; Propositions~\ref{prop:periodic-ns-role-localization}, \ref{prop:metric-divergence-skin-non-authority}, \ref{prop:quotient-visible-witness-vs-illicit-metric-gate}, and \ref{prop:boundary-licensing-same-scope-compatibility} & The manuscript now states exactly which Navier--Stokes observables are anchors, tensors, or skins on the live route, shows that metric divergence has no independent same-scope gate authority, and reconciles the non-generativity of licensed metric bookkeeping with the same-scope closure route.\\
Where is it stated that admissibility does \emph{not} supply the missing coercive estimate? & The Claim type and method class box; the Submission thesis paragraph; Remark~\ref{rem:partIII-claim-type-discipline}; Proposition~\ref{prop:no-additional-pde-side-criterion}; Theorem~\ref{thm:transfer-no-new-content} & The manuscript narrows the claim explicitly: admissibility constrains the licit same-scope status of purported failure, but does not by itself generate the analytic bridge inequality or a new continuation criterion.\\
Where is the primitive theorem packet proved locally? & \StructuralPacketRef{} and Appendix~A & P1--P4 are manuscript-local and fix the claim type before any periodic specialization.\\
\bottomrule
\end{tabularx}
\end{tcolorbox}

\begin{tcolorbox}[title={Theorem map for a first audit pass (continued)}, colback=blue!2!white, colframe=blue!55!black, boxsep=1pt, left=2pt, right=2pt, top=2pt, bottom=2pt]
\scriptsize
\renewcommand{\arraystretch}{1.08}
\setlength{\tabcolsep}{3pt}
\begin{tabularx}{\textwidth}{@{}L{0.28\textwidth}L{0.32\textwidth}Y@{}}
\toprule
\textbf{Question to check} & \textbf{Start here} & \textbf{What those labels settle}\\
\midrule
Why does that packet apply at fixed periodic scope, and where does the no-second-gate consequence actually enter? & Lemmas~\ref{lem:bridge-fixed-periodic-scope}, \ref{lem:bridge-admissible-side-ametric}, \ref{lem:bridge-periodic-live-admissibility}--\ref{lem:bridge-periodic-boundary-closure}, Theorem~\ref{thm:bridge-periodic-applicability}, Corollary~\ref{cor:periodic-unique-admissible-interior} & The bridge order is theorem-local and one-directional: 12C fixes bivalent non-degeneracy, 12D lawful redescription neutrality, 12E irreversibility, 12F fixed-periodic boundary-signature closure / scope-fixity, and 12G then applies P4. The no-second-gate consequence is therefore sourced from 12G/P4, not from 12F in isolation.\\
Where is the 12F / 12G / 13K / 20.5B / 20B / ST3 / 20C dependency chain audited in one place? & The Bridge-patch live dependency chain paragraph on page~1; Appendix~\ref{sec:bridge-patch-phase5-visibility-audit} & The no-new-criterion and standing / endpoint-status channels are exposed as one audited route: 12F remains live only as the fixed-periodic scope-fixity premise, 12G/P4 is the first exclusion node, 13K / 20.5B / 20B carry the no-new-criterion consequence, and ST2--ST3 / 20C.1 / 20C carry the same packet into endpoint-status language.\\
Where is same-scope exhaustion made finite and explicit? & Theorem~\ref{thm:13-5F-finite-same-scope-classification} through Corollary~\ref{cor:13-5L-rival-elimination}, then Theorem~\ref{thm:carrier-exhaustive-trichotomy} and Corollary~\ref{cor:derived-structural-exhaustion} & Every standing-positive same-scope rival on the typed carrier route is classified and eliminated before zero-parameter certification and carrier closure are used downstream; total same-scope endpoint closure is recovered only later through the dichotomy.\\
Where is the classical bridge isolated? & Propositions~\ref{prop:partIII-transport-only}, \ref{prop:no-hidden-transfer-hypothesis}, and \ref{prop:partIII-same-continuation-notion}; Theorem~\ref{thm:transport-realized-class-equals-official}; Theorems~\ref{thm:transfer-no-new-content} and \ref{thm:no-independent-classical-discriminator} & Part~III is theorem-local transfer: soundness, completeness, datum entry, fixed continuation notion, and no-new-criterion are separated rather than left in prose. The no-new-criterion content there is inherited from the 12G / P4 packet via Proposition~\ref{prop:no-additional-pde-side-criterion}, not from Lemma~\ref{lem:bridge-periodic-boundary-closure} in isolation.\\
Where is the standing/intelligibility packet proved locally? & Definition~\ref{def:st1-standing-positive-determination}; Theorems~\ref{thm:st2-intelligibility-standing-loss}, \ref{thm:st3-standing-admissibility-equivalence}, \ref{thm:carrier-to-lineage-binding}, and \ref{thm:no-admissibility-dynamics-realized-lineages}; Proposition~\ref{prop:standing-commitment-inheritance-realized-lineages}; Theorem~\ref{thm:st4-standing-conservation-realized-lineages} and Proposition~\ref{prop:st5-irreversibility-representational-commitment} & ST2 and ST3 are the first fixed-scope standing consequences downstream of 12G, which applies P4 after 12F's scope-fixity classification; carrier-to-lineage binding and the no-dynamics packet then transport that fixed-scope standing structure into the realized-lineage layer theorem-locally.\\
Where does ``outside admissible representability'' become a theorem-local branch? & Propositions~\ref{prop:exterior-endpoint-standing-failure} and \ref{prop:terminal-standing-failure-no-endpoint}; Theorem~\ref{thm:same-scope-continuation-failure-dichotomy}; Corollary~\ref{cor:outside-admissible-collapse-standing-failure} & An exterior same-scope endpoint is identified with terminal standing failure, and that branch is excluded locally rather than left as a neutral complaint.\\
Where is endgame completeness made local rather than inferential? & Theorem~\ref{thm:same-scope-continuation-failure-dichotomy}; Proposition~\ref{prop:same-scope-witness-exhaustion}; Lemma~\ref{lem:singular-image-induces-typed-candidate}; Theorem~\ref{thm:no-singular-image-certified-interior} & The endgame now splits explicitly: the standing-positive witness branch is exhausted locally, and the only other same-scope status is terminal standing failure.\\
Where is circularity between Part~II and Part~III blocked? & Corollary~\ref{cor:no-circular-burden-after-carrier-packet}; Propositions~\ref{prop:partIII-transport-only} and \ref{prop:partIII-same-continuation-notion} & The same-scope admissibility burden closes in Part~II before classical transfer begins, and Part~III uses that same continuation notion rather than feeding back a redefinition.\\
Where are the local PDE inputs proved? & Appendix~B: Proposition~\ref{prop:B1-mean-zero-poisson} through Corollary~\ref{cor:B8-local-analytic-packet} & The realization window, pressure normalization, classical upgrade, and overlap uniqueness are manuscript-local.\\
Where is the endpoint compressed to a short corollary? & Theorem~\ref{thm:no-singular-image-certified-interior}, Theorem~\ref{thm:primitive-to-classical-transfer-cascade}, Corollary~\ref{cor:official-periodic-structural-corollary}, Theorem~\ref{thm:official-periodic-pde-theorem} & The final classical statement is a short local restatement of an already completed primitive-to-classical chain.\\
\bottomrule
\end{tabularx}
\end{tcolorbox}

\begin{tcolorbox}[title={Compact glossary and PDE-language crosswalk}, colback=green!2!white, colframe=green!45!black, boxsep=1pt, left=2pt, right=2pt, top=2pt, bottom=2pt]
\scriptsize
\renewcommand{\arraystretch}{1.05}
\setlength{\tabcolsep}{2.8pt}
\begin{tabularx}{\textwidth}{@{}L{0.22\textwidth}L{0.35\textwidth}Y@{}}
\toprule
\textbf{Term or PDE phrase} & \textbf{Operational meaning in this manuscript} & \textbf{Local anchor}\\
\midrule
Same-scope & Fixed torus carrier, fixed viscosity, fixed Navier--Stokes equations, and only lawful bookkeeping skins or re-presentations. & Definitions~\ref{def:scope} and \ref{def:same-scope-continuation-mechanism}; bridge packet in Section~\ref{subsec:bridge-packet-periodic}\\
Same-scope continuation notion & The exact continuation question fixed in Part~II and then merely realized in Part~III: smooth periodic continuation on the declared torus carrier with the fixed gauge and lawful skins. & Lemma~\ref{lem:bridge-fixed-periodic-scope}; Corollary~\ref{cor:no-circular-burden-after-carrier-packet}; Proposition~\ref{prop:partIII-same-continuation-notion}\\
Section~12 bridge order / P4 application & The fixed periodic applicability ladder: 12C supplies bivalent non-degeneracy, 12D lawful redescription neutrality, 12E irreversibility, 12F boundary-signature-closure / same-scope typing, and 12G then applies P4 to that completed packet. & Lemma~\ref{lem:bridge-periodic-nondegeneracy}; Lemmas~\ref{lem:bridge-periodic-redescription-neutrality}--\ref{lem:bridge-periodic-boundary-closure}; Theorem~\ref{thm:bridge-periodic-applicability}\\
Bridge-patch dependency chain & The explicit audited route by which the Section~12 packet reaches the endgame: 12F remains a live bridge premise only in the role of fixed-scope typing, 12G / P4 yields the first no-second-gate consequence, 13K / 20.5B / 20B carry the no-new-criterion branch, and ST2--ST3 / 20C.1 / 20C carry the standing / endpoint-status branch. & Bridge-patch live dependency chain paragraph on page~1; Appendix~\ref{sec:bridge-patch-phase5-visibility-audit}; Appendix~\ref{sec:bridge-patch-phase6-lexical-audit}\\
Realized lineage as one same-scope determination & The maximal classical periodic solution attached to admitted carrier data, viewed as one same-scope object with one continuation question rather than a stack of independently reclassified time slices. & Definition~\ref{def:realized-lineage-same-object-convention}; Proposition~\ref{prop:partIII-same-continuation-notion}\\
Carrier-to-lineage binding & The theorem-local statement that the admitted carrier seed, its realized maximal classical evolution, and the fixed continuation question are one standing-bearing same-scope determination. & Theorem~\ref{thm:carrier-to-lineage-binding}; Proposition~\ref{prop:standing-commitment-inheritance-realized-lineages}\\
No admissibility dynamics on realized periodic lineages & Admissibility / standing on the realized periodic lineage is global rather than time-indexed: it cannot vary by slice number, restart stage, or horizon proximity while same scope is still claimed. & Theorem~\ref{thm:no-admissibility-dynamics-realized-lineages}; Corollary~\ref{cor:no-path-dependent-periodic-admissibility}\\
PDE-native admissibility packet & The theorem-local fact that the maximal classical realization already has fixed reference, same-object restart consistency, pre-horizon carrier re-entry, and an in-scope finite-horizon witness packet on $[0,T_*(x))$. & Theorem~\ref{thm:pde-native-admissibility-maximal-interval}; Theorem~\ref{thm:restart-consistency-same-object-persistence}; Corollary~\ref{cor:pre-horizon-slice-reentry}; Lemma~\ref{lem:finite-horizon-witness}\\
Standing quotient / future-behavior quotient & The fixed same-scope quotient whose classes are exactly the states indistinguishable by every admitted test after every admitted same-scope history. & Definition~\ref{def:future-behavior-congruence}; Theorem~\ref{thm:standing-quotient-future-behavior}\\
History-factorization & The theorem-local rule that admissibility and standing-bearing verdicts may depend only on the quotient state reached, not on path, order, or history representative. & Theorem~\ref{thm:history-factorization-no-path-dependent-admissibility}; Corollary~\ref{cor:no-path-dependent-periodic-admissibility}\\
Anchor / tensor / skin (forced roles) & Exhaustive same-scope role trichotomy: anchors change definedness or scope, tensors change quotient-visible standing consequences, and skin changes none. & Definition~\ref{def:forced-role-typing}; Theorem~\ref{thm:ats-role-minimality-no-fourth-role}; Corollary~\ref{cor:skin-non-authority-representative-diagnostics}\\
\bottomrule
\end{tabularx}
\end{tcolorbox}

\begin{tcolorbox}[title={Compact glossary and PDE-language crosswalk (continued)}, colback=green!2!white, colframe=green!45!black, boxsep=1pt, left=2pt, right=2pt, top=2pt, bottom=2pt]
\scriptsize
\renewcommand{\arraystretch}{1.05}
\setlength{\tabcolsep}{2.8pt}
\begin{tabularx}{\textwidth}{@{}L{0.22\textwidth}L{0.35\textwidth}Y@{}}
\toprule
\textbf{Term or PDE phrase} & \textbf{Operational meaning in this manuscript} & \textbf{Local anchor}\\
\midrule
Metric divergence / critical continuation norm & Licensed interior metric bookkeeping on the fixed periodic carrier. It carries standing-bearing force only when it is used as quotient-visible witness bookkeeping subordinate to the already fixed horizon witness; by itself it is not a same-scope gate. & Propositions~\ref{prop:metric-divergence-skin-non-authority} and \ref{prop:quotient-visible-witness-vs-illicit-metric-gate}; Proposition~\ref{prop:boundary-licensing-same-scope-compatibility}\\
Quotient-visible witness bookkeeping & Lawfully formed recorded quantity whose standing-bearing content is inherited from the already fixed pre-horizon witness, horizon discriminator, or singular-candidate extractor, rather than from a new metric selector or continuation gate. & Definition~\ref{def:quotient-visible-witness-bookkeeping}; Proposition~\ref{prop:quotient-visible-witness-vs-illicit-metric-gate}\\
Standing-positive & Admitted by the fixed gate and therefore capable of carrying theorem-local consequence inside the declared scope; in the hardened fixed-periodic form, this means satisfying the standing conditions recorded in ST1. & Definitions~\ref{def:standing}, \ref{def:admissible-interior}, and \ref{def:st1-standing-positive-determination}\\
Admissible interior & The standing-positive regime at fixed scope; in the periodic specialization, the unique admitted side of the fixed periodic problem. & Definition~\ref{def:admissible-interior}; Corollary~\ref{cor:periodic-unique-admissible-interior}\\
Standing-neutral drift & A purported same-scope realized evolution from standing-positive status to a neutral non-standing terminal status; ST4 rules this out on realized periodic lineages. & Theorem~\ref{thm:st4-standing-conservation-realized-lineages}\\
Standing-failure branch & The same-scope terminal status obtained when an alleged endpoint can be formulated only by leaving admissible representability; this is standing-negative inadmissibility, not a neutral exterior remainder. & Propositions~\ref{prop:exterior-endpoint-standing-failure} and \ref{prop:terminal-standing-failure-no-endpoint}\\
Representational commitment & The standing-bearing same-scope reference anchor carried by a realized lineage and not admissibly retractable once realization is underway. & Definition~\ref{def:standing-bearing-representational-commitment}; Proposition~\ref{prop:st5-irreversibility-representational-commitment}\\
Endpoint-status trichotomy / no-third-status collapse & The realized-lineage endgame theorem: any same-scope finite-horizon endpoint proposal is either a standing-positive carrier witness, terminal standing failure, or an illicit same-scope gate / scope move, and only the witness branch remains as a licit same-scope endpoint status. & Theorem~\ref{thm:same-scope-continuation-failure-dichotomy}; Corollary~\ref{cor:no-third-same-scope-endpoint-status}\\
Standard periodic carrier & The fixed-scope Navier--Stokes object class later identified with the unique admissible interior. & Definition~\ref{def:standard-carrier}; Theorem~\ref{thm:periodic-carrier-unique-interior}\\
Official periodic datum & Smooth divergence-free periodic initial datum in Fefferman's statement~(B). & Definition~\ref{def:official-periodic-data}\\
Realized local classical class & The ordinary local smooth Navier--Stokes solution class obtained from admitted carrier data by the realization map. & Theorems~\ref{thm:local-classical-realization} and \ref{thm:transport-realized-class-equals-official}\\
Continuation discriminator & Same-scope witness that marks or governs continuation failure at the horizon on the fixed carrier. & Definition~\ref{def:horizon-continuation-discriminator}; \HorizonDetectabilityRef{}\\
Singular candidate & Typed carrier object representing a hypothetical standing-positive singular breakdown witness. & Definition~\ref{def:singular-candidate}; Lemma~\ref{lem:singular-image-induces-typed-candidate}\\
Branch set & Nonempty forced subset of \{S1,S2,S3,S4,S5\} describing how an impossible same-scope escape would have to present itself. & Definition~\ref{def:branch-forcing-set}; Theorem~\ref{thm:constructive-branch-forcing}\\
Official periodic theorem & The classical PDE restatement of the already-proved structural endpoint. & Corollary~\ref{cor:official-periodic-structural-corollary}; Theorem~\ref{thm:official-periodic-pde-theorem}\\
\bottomrule
\end{tabularx}
\end{tcolorbox}

\begin{tcolorbox}[breakable, title={Compressed proof spine for the official theorem}, colback=blue!2!white, colframe=blue!55!black, boxsep=1pt, left=2pt, right=2pt, top=2pt, bottom=2pt]
\textbf{Only live route.} The list below expands the same page-1 chain 19C--19F $\to$ 20B $\to$ ST4/ST5 $\to$ 20C $\to$ 21.x; no separate proof route is used for the official theorem. For the specific 12F / 12G seam, the carried channels are likewise explicit and unique: 12F $\to$ 12G/P4 $\to$ 13K $\to$ 20.5B $\to$ 20B on the no-new-criterion side, and 12F $\to$ 12G/P4 $\to$ ST2--ST3 $\to$ 20C.1 $\to$ 20C on the standing / endpoint-status side; Appendix~\ref{sec:bridge-patch-phase5-visibility-audit} audits both channels node by node.

\begin{enumerate}[label=(\roman*), leftmargin=2.2em, itemsep=0.15em, topsep=0.15em]
\item \textbf{Primitive packet + bridge:} \StructuralPacketRef{} together with the bridge packet of Section~\ref{subsec:bridge-packet-periodic} prove live admissibility and the remaining bridge antecedents theorem-locally, with 12C--12F completing the fixed periodic bridge packet and 12G then applying P4 at that fixed scope; only after that one-directional bridge order is in place does the unique admissible interior follow.
\item \textbf{Finite same-scope exhaustion + carrier identification:} Theorem~\ref{thm:13-5F-finite-same-scope-classification} through Corollary~\ref{cor:13-5L-rival-elimination}, then Theorem~\ref{thm:ns-carrier-verifies-rule-package}, Theorem~\ref{thm:periodic-carrier-unique-interior}, Corollary~\ref{cor:no-circular-burden-after-carrier-packet}, and Corollary~\ref{cor:derived-structural-exhaustion}, certify the standard periodic carrier and eliminate standing-positive same-scope rivals before the later dichotomy closes the complementary branch.
\item \textbf{Transfer soundness + completeness:} official data enter the admitted carrier class, the realized maximal classical object is fixed as one same-scope lineage with the same continuation notion preserved into Part~III, and the realized local class equals the full official local classical class by Corollary~\ref{cor:every-official-datum-admitted}, Definition~\ref{def:realized-lineage-same-object-convention}, Propositions~\ref{prop:no-hidden-transfer-hypothesis} and \ref{prop:partIII-same-continuation-notion}, and Theorem~\ref{thm:transport-realized-class-equals-official}.
\item \textbf{PDE-native admissibility on the realized interval:} standard local periodic theory already forces fixed reference, same-object restart consistency, pre-horizon carrier re-entry, and an in-scope pre-horizon witness of any finite-horizon failure by Theorem~\ref{thm:pde-native-admissibility-maximal-interval}, Theorem~\ref{thm:restart-consistency-same-object-persistence}, Corollary~\ref{cor:pre-horizon-slice-reentry}, and Lemma~\ref{lem:finite-horizon-witness}.
\item \textbf{Quotient / history / ATS packet:} same-scope identity is fixed by the future-behavior quotient, every standing-relevant same-scope discriminator factors through that quotient, admissibility cannot depend on path or order inside a standing class, and representative-only skin carries no standing authority by Theorems~\ref{thm:standing-quotient-future-behavior}, \ref{thm:factorization-discipline-same-scope}, \ref{thm:history-factorization-no-path-dependent-admissibility}, and \ref{thm:ats-role-minimality-no-fourth-role}, together with Corollary~\ref{cor:skin-non-authority-representative-diagnostics} and Proposition~\ref{prop:periodic-carrier-interface-quotient-history}.
\item \textbf{Metric / tensor / witness localization:} the actual periodic Navier--Stokes observables used on the live route are role-localized, metric divergences have no independent same-scope gate authority, and any load-bearing norm-growth statement is licit only as quotient-visible witness bookkeeping subordinate to the already fixed horizon witness by Table~\ref{tab:periodic-ns-role-localization}, Definition~\ref{def:quotient-visible-witness-bookkeeping}, and Propositions~\ref{prop:periodic-ns-role-localization}, \ref{prop:metric-divergence-skin-non-authority}, \ref{prop:quotient-visible-witness-vs-illicit-metric-gate}, and \ref{prop:boundary-licensing-same-scope-compatibility}.
\item \textbf{Transfer no-new-criterion + detectability:} classical realization adds no new standing-positive same-scope continuation content on the live route and any hypothetical breakdown is already carrier-visible by Theorem~\ref{thm:transfer-no-new-content}, Corollary~\ref{cor:breakdown-carrier-visible}, \HorizonDetectabilityRef{}, and Theorem~\ref{thm:no-independent-classical-discriminator}; the no-new-criterion component on this live route is inherited from the fixed-periodic P4 application through Proposition~\ref{prop:no-additional-pde-side-criterion}, not from Lemma~\ref{lem:bridge-periodic-boundary-closure} alone.
\item \textbf{Carrier-to-lineage binding + no admissibility dynamics:} ST2 and ST3 first transport the fixed-scope standing packet downstream from the 12G / P4 bridge, and then the admitted carrier seed, its realized maximal classical evolution, and the fixed continuation question are shown to be one standing-bearing same-scope determination whose admissibility cannot vary by time, slice, restart stage, or horizon proximity by Theorems~\ref{thm:carrier-to-lineage-binding} and \ref{thm:no-admissibility-dynamics-realized-lineages}, together with Proposition~\ref{prop:standing-commitment-inheritance-realized-lineages} and the realized-lineage packet ST4--ST5.
\item \textbf{Realized-lineage endpoint-status trichotomy / collapse:} Propositions~\ref{prop:exterior-endpoint-standing-failure} and \ref{prop:terminal-standing-failure-no-endpoint}, Theorem~\ref{thm:same-scope-continuation-failure-dichotomy}, and Corollary~\ref{cor:no-third-same-scope-endpoint-status} show that any alleged finite-horizon endpoint proposal is either a standing-positive carrier witness, terminal standing failure, or an illicit same-scope gate / scope move, and that only the witness branch remains as a licit same-scope endpoint status.
\item \textbf{Branch forcing + exclusion:} Theorem~\ref{thm:constructive-branch-forcing}, Proposition~\ref{prop:same-scope-witness-exhaustion}, Lemma~\ref{lem:singular-image-induces-typed-candidate}, Propositions~\ref{prop:no-illicit-singular-image} and \ref{prop:no-quotient-visible-singular-image}, and Corollary~\ref{cor:no-third-branch} eliminate every standing-positive same-scope singular image arising from admitted carrier states.
\item \textbf{Endpoint corollary + official restatement:} Theorem~\ref{thm:no-singular-image-certified-interior} feeds the short transfer cascade Theorem~\ref{thm:primitive-to-classical-transfer-cascade}, then Corollary~\ref{cor:official-periodic-structural-corollary} and Theorem~\ref{thm:official-periodic-pde-theorem}.
\end{enumerate}
Appendix~\ref{sec:internal-ledger} contains the non-load-bearing support ledger, the Phase-0 source freeze and source-role matrix, the referee question matrix, and the provenance / quarantine notes. Those pages summarize the proof and point back to local labels; they do not carry any live theorem burden. The standing/intelligibility packet ST1--ST5 and the realized-lineage endpoint-status trichotomy / collapse are now proved inside the paper itself, so the standing-failure and illicit same-scope branches are no longer off-manuscript escapes and no conflicting corpus line may enter the endpoint chain by title alone.
\end{tcolorbox}

\begin{tcolorbox}[title={Denial map: what must be denied to keep each objection alive}, colback=blue!2!white, colframe=blue!55!black, boxsep=1pt, left=2pt, right=2pt, top=2pt, bottom=2pt]
\scriptsize
\renewcommand{\arraystretch}{1.08}
\setlength{\tabcolsep}{3pt}
\begin{tabularx}{\textwidth}{@{}L{0.33\textwidth}L{0.31\textwidth}Y@{}}
\toprule
\textbf{Objection to keep alive} & \textbf{Must deny at least one of} & \textbf{Why this is the right denial target}\\
\midrule
There is a residual same-scope singularity witness outside the paper's extraction. & Proposition~\ref{prop:same-scope-witness-exhaustion}; Theorem~\ref{thm:no-independent-classical-discriminator}; Corollary~\ref{cor:derived-structural-exhaustion} & The manuscript now states locally that every standing-positive same-scope breakdown witness entering the live endgame is exhausted by the horizon discriminator and its induced branch data.\\
The manuscript is really claiming admissibility itself supplies the missing analytic bridge inequality. & The Claim type and method class box; the Submission thesis paragraph; Remark~\ref{rem:partIII-claim-type-discipline}; Proposition~\ref{prop:no-additional-pde-side-criterion}; Theorem~\ref{thm:transfer-no-new-content} & The paper now says the opposite on the page: it claims only a same-scope status impossibility theorem for purported finite-horizon failure, not a new coercive estimate or analytic bridge inequality.\\
Lemma~\ref{lem:bridge-periodic-boundary-closure} is still acting as the standalone no-second-gate engine. & Theorem~\ref{thm:bridge-periodic-applicability}; Proposition~\ref{prop:no-additional-pde-side-criterion}; Theorems~\ref{thm:transfer-no-new-content} and \ref{thm:no-independent-classical-discriminator}; Theorem~\ref{thm:st3-standing-admissibility-equivalence}; Proposition~\ref{prop:exterior-endpoint-standing-failure}; Appendix~\ref{sec:bridge-patch-phase5-visibility-audit} & The manuscript now advertises and audits the bridge as a one-directional chain: 12F remains live only as the fixed-scope typing premise, 12G applies P4 and is the first exclusion node, 13K / 20.5B / 20B carry the no-new-criterion consequence, and ST2--ST3 / 20C.1 / 20C carry the standing / endpoint-status consequence. Keeping the objection alive therefore requires denying that audited chain or denying 12F as a legitimate bridge premise, not merely quoting 12F in isolation.\\
The realized lineage should be treated as a sequence of independently reclassified time slices rather than one same-scope object. & Definition~\ref{def:realized-lineage-same-object-convention}; Proposition~\ref{prop:partIII-same-continuation-notion}; Theorem~\ref{thm:carrier-to-lineage-binding}; the Same-object convention paragraph on page~1 & The submission now fixes its object of proof explicitly and theorem-locally: one realized maximal classical lineage with one same-scope continuation question, bound to its admitted carrier seed as a single standing-bearing determination. Denying that changes the thesis rather than exposing a hidden gap.\\
The solution is admissible before $T_*(x)$ but falls out of admissibility at the horizon while same scope is still claimed. & Theorems~\ref{thm:carrier-to-lineage-binding} and \ref{thm:no-admissibility-dynamics-realized-lineages}; Proposition~\ref{prop:standing-commitment-inheritance-realized-lineages}; Corollary~\ref{cor:no-path-dependent-periodic-admissibility} & The manuscript now proves locally that same-scope admissibility on a realized periodic lineage is global rather than time-indexed. The quoted sentence is therefore not a neutral same-scope option: it is either an ill-typed time/path-dependent reclassification, a skin-to-authority move, or an illicit new gate.\\
The dynamical carrier is merely assumed, not proved, to satisfy the minimal standing / admissibility content on $[0,T_*(x))$. & Theorem~\ref{thm:pde-native-admissibility-maximal-interval}; Theorem~\ref{thm:restart-consistency-same-object-persistence}; Corollary~\ref{cor:pre-horizon-slice-reentry}; Lemma~\ref{lem:finite-horizon-witness} & These labels now derive the pre-horizon fixed-reference, restart, re-entry, and witness packet directly from standard local periodic theory; denying that packet requires contesting those local theorems rather than asserting that admissibility was simply imported into the dynamics.\\
Admissibility or continuation status may depend on path, order, or representative choice inside one same-scope state. & Theorems~\ref{thm:standing-quotient-future-behavior}, \ref{thm:factorization-discipline-same-scope}, and \ref{thm:history-factorization-no-path-dependent-admissibility}; Corollary~\ref{cor:no-path-dependent-periodic-admissibility}; Corollary~\ref{cor:skin-non-authority-representative-diagnostics} & The manuscript now proves locally that same-scope standing-relevant verdicts factor through the fixed quotient and cannot be changed by path/order dependence or by representative-only skin.\\
\bottomrule
\end{tabularx}
\end{tcolorbox}

\begin{tcolorbox}[title={Denial map: what must be denied to keep each objection alive (continued)}, colback=blue!2!white, colframe=blue!55!black, boxsep=1pt, left=2pt, right=2pt, top=2pt, bottom=2pt]
\scriptsize
\renewcommand{\arraystretch}{1.08}
\setlength{\tabcolsep}{3pt}
\begin{tabularx}{\textwidth}{@{}L{0.33\textwidth}L{0.31\textwidth}Y@{}}
\toprule
\textbf{Objection to keep alive} & \textbf{Must deny at least one of} & \textbf{Why this is the right denial target}\\
\midrule
Metric divergence or fixation failure by itself carries same-scope singularity authority. & Table~\ref{tab:periodic-ns-role-localization}; Definition~\ref{def:quotient-visible-witness-bookkeeping}; Propositions~\ref{prop:periodic-ns-role-localization}, \ref{prop:metric-divergence-skin-non-authority}, and \ref{prop:quotient-visible-witness-vs-illicit-metric-gate} & The manuscript now localizes the actual Navier--Stokes observables as anchors, tensors, or skins on the live route. A norm blow-up statement is standing-bearing only as bookkeeping subordinate to the fixed horizon witness; if promoted beyond that role it becomes an illicit extra gate or scope change.\\
The periodic bridge never proves live admissibility; it only gestures at non-vacuity. & Lemmas~\ref{lem:bridge-periodic-live-admissibility} and \ref{lem:bridge-periodic-nondegeneracy}; Theorem~\ref{thm:bridge-periodic-applicability}; Corollary~\ref{cor:periodic-unique-admissible-interior} & Live admissibility is now verified by an explicit periodic same-scope admissibility judgement and is fed theorem-locally into the bridge and unique-interior corollary.\\
The breakdown exists but only outside admissible representability. & Propositions~\ref{prop:exterior-endpoint-standing-failure} and \ref{prop:terminal-standing-failure-no-endpoint}; Theorem~\ref{thm:same-scope-continuation-failure-dichotomy}; Corollary~\ref{cor:outside-admissible-collapse-standing-failure} & ``Outside admissible representability'' is now a theorem-local standing-failure branch rather than a neutral remainder, and that branch cannot complete the same-scope endpoint of a standing-positive realized lineage.\\
Classical realization adds a hidden continuation criterion after carrier certification. & Theorem~\ref{thm:transfer-no-new-content}; Theorem~\ref{thm:no-independent-classical-discriminator} & Any surviving PDE-side continuation gate would have to break one of the two no-new-criterion statements.\\
Part~III silently changes the continuation notion fixed in Part~II. & Corollary~\ref{cor:no-circular-burden-after-carrier-packet}; Propositions~\ref{prop:partIII-transport-only} and \ref{prop:partIII-same-continuation-notion} & The handoff is now theorem-local: the same continuation notion fixed in the bridge and carrier packet is realized in Part~III without redefinition.\\
The breakdown witness is visible but unusable in the branch-forcing theorem. & Lemma~\ref{lem:propagation-standing-positive-slices}; Corollary~\ref{cor:breakdown-carrier-visible}; \HorizonDetectabilityRef{}; Lemma~\ref{lem:singular-image-induces-typed-candidate} & The witness must be standing-positive on the fixed carrier before branch forcing can apply. Those are the exact labels that supply that handoff.\\
The final impossibility theorem is broader than the branches actually excluded. & Theorem~\ref{thm:constructive-branch-forcing}; Propositions~\ref{prop:no-illicit-singular-image} and \ref{prop:no-quotient-visible-singular-image}; Corollary~\ref{cor:no-third-branch} & The no-singular-image theorem is only as broad as the explicit branch-forcing and branch-elimination packet.\\
The standing/intelligibility burden still lives only in companion papers. & Definition~\ref{def:st1-standing-positive-determination}; Theorems~\ref{thm:st2-intelligibility-standing-loss}, \ref{thm:st3-standing-admissibility-equivalence}, and \ref{thm:st4-standing-conservation-realized-lineages}; Proposition~\ref{prop:st5-irreversibility-representational-commitment} & The fixed-scope and realized-lineage standing/intelligibility packet is now carried by named local definitions and theorems inside the submitted PDF.\\
A fixation-persistence or post-closure corpus sentence still undercuts the submission from outside the PDF. & Appendix~\ref{sec:phase0-source-freeze}; Proposition~\ref{prop:three-level-support-ledger}; Proposition~\ref{prop:boundary-licensing-same-scope-compatibility} & Phase~0 freezes the live source pool, and Phase~5 internalizes the only compatibility statement the submission needs: licensed metric bookkeeping is non-generative, but same-scope admissibility still governs the licit status of singularity representations. External titles therefore remain provenance or contrast only and cannot silently rewrite the endpoint chain.\\
The endpoint does not answer Fefferman~(B). & Theorem~\ref{thm:primitive-to-classical-transfer-cascade}; Corollary~\ref{cor:official-periodic-structural-corollary}; Theorem~\ref{thm:official-periodic-pde-theorem} & These labels compress the whole carrier-side contradiction into the official classical statement.\\
\bottomrule
\end{tabularx}
\end{tcolorbox}

\tableofcontents

\newpage