% PAGE-BUDGET TARGET: 3 pages
% HARD MAX: 3 pages
% BLUEPRINT PHASE 4: Draft Sections 7--8 and Appendix B.
\section{Assembly of the main theorem}\label{sec:assembly}
\budgetnote{3}{3}

We now assemble \cref{thm:main} from the packet stack stated in Sections~\ref{sec:uv}--\ref{sec:endpoint}. No new analytic input enters here. Each part of the theorem follows by concatenating the already named ultraviolet, Route~1, Lane~A, QE3, and endpoint packets in the order fixed by the public proof spine.

\begin{proof}[Proof of \cref{thm:main}]
\textbf{Part~(A).} The ultraviolet/public-scope gate of Section~\ref{sec:uv} furnishes the compact-simple A1 theorem \cref{thm:uv-gate}, the public group-scope export Corollary~\ref{cor:group-scope-export}, and the one-shot entrance theorem Proposition~\ref{prop:one-shot-entrance}. Those three results are exactly the theorem-level input required for the one-shot entrance statement in \cref{thm:main}(A). The faithful-$\rho$ scope caveat and the effective-group boundary were fixed already in Section~\ref{sec:scope} and are preserved unchanged.

\textbf{Part~(B).} The Euclidean clustering statement in \cref{thm:main}(B) is downstream of the vacuum-gap chain. Once the continuum sharp-local gap of Corollary~\ref{cor:continuum-vacuum-gap} is known, the standard OS semigroup estimate on a dense positive-time probe core yields exponential decay at rate $m_*$. This is a consequence of the same sharp-local OS state used throughout the paper and does not add a second gap proof.

\textbf{Part~(C).} Lane~A closes the constructive route to the full sharp-local algebra through the flowed-state and bounded-base packet \cref{thm:flowed-state,cor:bounded-base-state}, the exact-dimension quotient and finite-truncation packet \cref{thm:exact-dimension-identity,thm:quotient-coefficient-extraction,thm:one-shell-transport,thm:finite-truncation-inverse,cor:finite-truncation-sfte}, the mixed-channel finite-cap closure node \cref{thm:mixed-correlator-closure}, the finite-cap sharp-local extension \cref{thm:finite-cap-extension}, the inductive-union passage Corollary~\ref{cor:full-inductive-union}, and bounded-base cyclicity \cref{thm:bounded-base-cyclicity}. The claim-facing endpoint packet of Section~\ref{sec:endpoint} then yields the Euclidean OS dossier \cref{thm:euclidean-os-dossier}, the Wightman--Haag--Kastler reconstruction \cref{thm:wightman-reconstruction}, the field correspondence Corollary~\ref{cor:field-correspondence}, and the non-triviality witness \cref{thm:nontriviality}. Together these give \cref{thm:main}(C).

\textbf{Part~(D).} Route~1 produces the tuned fixed-lattice OS gap Proposition~\ref{prop:lattice-gap}, returns it to the physical Wilson theory through \cref{thm:wilson-return}, and seals the weak-window intake with the sole live certificate \cref{thm:weak-window-certificate}. The final transport chain is then exactly the bounded Wilson limit \cref{thm:bounded-wilson-os-limit}, the continuum-time OS upgrade \cref{thm:continuum-time-os-upgrade}, the density and graph-core handoff Corollary~\ref{cor:density-bounded-base} and Lemma~\ref{lem:qe3-graph-core}, the unique transport node \cref{thm:continuum-gap-transport}, and the continuum sharp-local vacuum-gap corollary Corollary~\ref{cor:continuum-vacuum-gap}. This proves \cref{thm:main}(D).

Finally, the theorem-level endpoint and the faithful-Wilson caveat are fixed by \cref{thm:faithful-wilson-hypotheses,thm:faithful-wilson-universality,cor:rho-indexed-ledger,thm:exact-local-net-endpoint,cor:group-only-endpoint}. Thus the theorem proved in \cref{thm:main} is exactly a theorem about the bounded-region local gauge-invariant sharp-local net attached to the compact connected simple group $G$, with faithful-Wilson universality at the level of the continuum local theory and a still-$\rho$-indexed explicit Route~1 quantitative certificate.
\end{proof}

This completes the proof of \cref{thm:main}. The core paper has now done its intended job: it has exposed the claim, the exact theorem-level endpoint, the finite public packet reduction, and the decisive seam closures, while the detailed analytic and constructive proofs live in stable companion papers.
