\documentclass[preprint,aip,jmp,amsmath,amssymb,nofootinbib]{revtex4-2}
\input{shared/packages}
\input{shared/theorems}
\input{shared/macros}
\makeatletter\input{shared/external_labels_companion1.auxinc}\makeatother
\SuiteSetupMetadata{Companion I: Ultraviolet Gate and Route~1 Mass-Gap Chain}
\makeatletter
\def\input@path{{source/}{source/sections/}{source/appendices/}{source/clean_build/}}
\makeatother
\begin{document}
\SuiteMakeFrontMatter{Companion I: Ultraviolet Gate and Route~1 Mass-Gap Chain}
\begin{abstract}
This companion is the proof home for the ultraviolet/public-scope gate and the Route~1 mass-gap chain. It is assembled directly from the canonical March~16,~2026 LaTeX source tree. The document preserves the theorem-facing routing used by the core paper and incorporates the authoritative same-scale Wilson return block, the live Route~1 closure file, the compact-simple ultraviolet packet, and the associated worked audits and ledgers from the canonical source.
\end{abstract}
\maketitle
\section*{Lean verification note}
Within the accompanying Lean repository, the Route~1 / mass-gap side of the
current formalization is no longer represented only as a structural routing
surface. It is packaged through the native theorem-object and compatibility
layers culminating in the full manuscript-facing package boundary
\texttt{YangMillsFullManuscriptNativePackageExportStatement}. The Lean layer is
meant to help a referee inspect theorem flow, source-label anchoring, and the
placement of the present companion inside the full proof architecture.
\section*{Guide to proof homes}
This companion keeps the theorem-facing proof homes attached to the canonical manuscript source. Section~III of the original manuscript supplies the same-scale Wilson return block; Appendix~F supplies the live Route~1 closure file; Appendix~N supplies the compact-simple ultraviolet packet; and Appendices~G--K supply the associated worked audits and ledgers.

\paragraph{Phase-I proof-surface freeze.}
The live proof burden of the hardened suite is carried only by the four compiled roots and the theorem-facing appendices compiled inside them. Support PDFs, archival source facsimiles not compiled in those roots, source-only routing appendices, build notes, and editorial memoranda are reserve materials only: they add no mathematics, carry no unique proof step, and are not part of the proof burden. The authoritative live routing references are the core-paper packet-docket appendix and Phase-I freeze appendix.

\paragraph{Phase-II seam repair.}
The QE3 transport seam is now frozen with the literal role split required by the closure plan. In Appendix~F, Source Corollary~5.75 is used only for bounded-state restriction compatibility, Source Theorem~5.74(b) supplies the finite-cap sharp-local OS structure, Source Corollary~5.76 is the separate inductive-union passage, and Corollary~F.213 together with Lemma~F.214 remains the later density/graph-core handoff. No Route~1 statement in this companion treats Source Corollary~5.75 as the inductive-union theorem.

\paragraph{Phase-IV quantifier and transport hardening.}
The same-scale Wilson return block is to be read with logarithmic-depth uniformity only: the live theorem-facing estimate is uniform for dyadic depths $m\le C\log(1/u(a))$, exactly the regime later used for one-shot entrance and fixed-physical-scale comparison, and it should neither be paraphrased as a merely fixed-depth statement nor overread as an arbitrary-depth theorem. In Appendix~F the QE3 route is frozen equally literally: Theorem~F.211 records only bounded dyadic OS limits on $\mathcal A_+$, Theorem~F.212 is the unique dyadic-to-all-$t$ upgrade via the Lane~A sharp-local semigroup, Corollary~F.213 supplies density of the bounded base algebra, Lemma~F.214 supplies the finite-cap graph-core package, and Theorem~F.216 performs the actual continuum gap transfer.

\paragraph{Phase-V measure pipeline localization.}
The concise theorem-level Route~1 measure pipeline ledger appears immediately below, while Section~III remains the proof home for the underlying factorization and transport theorems. Theorem~\ref{thm:wilson_one_step_factorization} is the exact one-step conditional expectation / block-factorization node, Theorem~\ref{thm:wilson_exact_recursion} is the nested conditional-expectation node, Proposition~\ref{prop:averaged_bad_event_transport} is the averaged bad-event transport estimate on one fixed support hull, Proposition~\ref{prop:laneC_transport_identification} states that the actual chart-truncated Lane~C recursion makes precisely that truncation-only substitution and no other measure-side change, and Theorem~\ref{thm:Wilson_patch_transport} is the sole theorem-level Wilson-to-patched return later consumed on the public Route~1 spine.

\paragraph{Phase-III proof-home crosschecks.}
\begin{center}
\small
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.08}
\begin{tabular}{@{}p{0.95cm}p{1.2cm}p{4.0cm}p{4.2cm}@{}}
\toprule
\textbf{Core label} & \textbf{Source label} & \textbf{Proof home} & \textbf{First downstream use in the core}\\
\midrule
III.3 & F.317, F.318 & Appendix~F (QE1 one-shot entrance block) & Core Proposition~III.3\\
IV.1 & F.308 & Appendix~F (QE2$_{\mathrm{lat}}$ closure block) & Core Proposition~IV.1\\
IV.2 & III.18 & Section~III (same-scale Wilson return block) & Core Theorem~IV.2\\
IV.4 & F.298 & Appendix~F (weak-window sufficiency certificate) & Core Theorem~IV.4 and then the transport ledger in Section~VI\\
VI.1 & F.211 & Appendix~F (bounded Wilson / dyadic OS limit) & Core Theorem~VI.1 and then Core Theorem~VI.2\\
VI.2 & F.212 & Appendix~F (continuum-time OS upgrade block) & Core Theorem~VI.2 and then Core Theorem~VI.7\\
VI.4 & F.213 & Appendix~F (density export) & Core Corollary~VI.4 and then Core Lemma~VI.5\\
VI.5 & F.214 & Appendix~F (graph-core handoff) & Core Lemma~VI.5 and then Core Theorem~VI.7\\
VI.7 & F.216 & Appendix~F (continuum vacuum-gap transport) & Core Theorem~VI.7 and then Core Corollary~VI.8\\
VI.8 & F.5 & Appendix~F (continuum vacuum-gap corollary) & Core Corollary~VI.8 and then Main Theorem~I.1(B,D) and the endpoint packet\\
\bottomrule
\end{tabular}
\end{center}

\section{Route~1 measure pipeline ledger}
This section isolates the exact measure-theoretic packet consumed later by the same-scale Wilson return theorem. Its role is theorem-facing rather than expository: it records only the conditional-expectation, factorization, and averaged transport nodes actually used downstream on the public Route~1 spine.

\begin{proposition}[Phase-V Route~1 measure pipeline ledger]\label{prop:route1_measure_pipeline_ledger}
For the fixed-scale Route~1 test class later consumed by Theorem~\ref{thm:Wilson_patch_transport}, the live measure-transport chain is exactly the following.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.25em]
\item Theorem~\ref{thm:wilson_one_step_factorization} identifies the exact Wilson one-step fluctuation law as a conditional block-product law once the dyadic skeleton variables are frozen.
\item Theorem~\ref{thm:wilson_exact_recursion} iterates those conditional expectations and identifies the depth-$m$ Wilson evaluation with the exact blocked conditional-expectation recursion.
\item Proposition~\ref{prop:averaged_bad_event_transport} proves the one-step averaged transport estimate obtained by conditioning only on the local good-block event on one fixed support hull.
\item Proposition~\ref{prop:laneC_transport_identification} states that the actual chart-truncated Lane~C recursion changes only the one-step fluctuation integration operators by the truncation $T_{j+1}\mapsto T_{j+1}^{\mathrm{good}}$, while Proposition~\ref{prop:local_transport_closure} together with Proposition~\ref{prop:depatch_finite_depth} propagates that one-step averaged estimate through the admissible finite logarithmic depth.
\item Consequently Theorem~\ref{thm:Wilson_patch_transport} is the sole theorem-level Wilson-to-patched return later consumed on the public Route~1 spine.
\end{enumerate}
No later Route~1 theorem uses any stronger conditional-expectation, factorization, or measure-transport input than this packet.
\end{proposition}

\proofhome{Section~III below, in particular Theorem~\ref{thm:wilson_one_step_factorization}, Theorem~\ref{thm:wilson_exact_recursion}, Proposition~\ref{prop:averaged_bad_event_transport}, Proposition~\ref{prop:local_transport_closure}, Proposition~\ref{prop:depatch_finite_depth}, Proposition~\ref{prop:laneC_transport_identification}, and Theorem~\ref{thm:Wilson_patch_transport}.}
\dependencyledger
  {Theorem~\ref{thm:wilson_one_step_factorization}, Theorem~\ref{thm:wilson_exact_recursion}, Proposition~\ref{prop:averaged_bad_event_transport}, Proposition~\ref{prop:local_transport_closure}, Proposition~\ref{prop:depatch_finite_depth}, Proposition~\ref{prop:laneC_transport_identification}, and Theorem~\ref{thm:Wilson_patch_transport}}
  {none}
  {on the fixed-scale Route~1 test class, the Wilson-to-patched seam uses only the exact conditional-expectation / block-factorization packet together with the averaged bad-event transport bound propagated through finite logarithmic depth; no stronger measure-side statement is hidden downstream}
  {Theorem~\ref{thm:Wilson_patch_transport}, Theorem~\ref{thm:weak_window_sufficiency}, and the QE3 transport route in Appendix~F}

\setcounter{section}{2}
\input{source/sections/02_reflection.tex}
\appendix
\setcounter{section}{5}
\input{source/appendices/appendixF_mass_gap.tex}
\clearpage
\input{source/appendices/appendixG_one_plaquette_sp.tex}
\input{source/appendices/appendixH_one_plaquette_spinodd.tex}
\input{source/appendices/appendixI_one_plaquette_spineven.tex}
\input{source/appendices/appendixJ_TP_tools.tex}
\input{source/appendices/appendixK_parameter_schedule.tex}
\setcounter{section}{13}
\input{source/appendices/appendixN_group_scope_completion.tex}
\SuiteDataAvailabilitySection
\input{shared/bibliography}
\end{document}
